---
title: "Factorial desing"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
author: Julio Iturra
output: 
  html_document:
     theme: flatly
     highlight: tango
     toc: true
     toc_float: true
     toc_depth: 2
     number_sections: false
     code_folding: hide
editor_options: 
  chunk_output_type: console
---
# Vignette design

1. [Draft Google Docs](https://docs.google.com/document/d/1Tn_vZTNaxIOeK5lHcQkPWt3Knw_OqKIEe7pPf19CI4c/edit) 
2. Code in SAS (https://odamid-euw1.oda.sas.com/)
3. Macro (https://support.sas.com/rnd/app/macros/MktEx/MktEx.pdf)

```{r, eval=FALSE, include=TRUE}
%mktruns(2 3 3 4 3 3 3 4 4)
Saturated      = 21                                       
Full Factorial = 31,104                                   
Some Reasonable                      Cannot Be            
   Design Sizes       Violations     Divided By           
            144 *              0                          
             72                3     16                   
            216                3     16                   
             36                6      8 16                
            108                6      8 16                
            180                6      8 16                
             48               10      9                   
             96               10      9                   
            192               10      9                   
             24               13      9 16                
             21 S             40      2  4  6  8  9 12 16 
 - 100% Efficient design can be made with the MktEx macro.
 - Saturated Design - The smallest design that can be made.
   Note that the saturated design is not one of the       
   recommended designs for this problem.  It is shown     
   to provide some context for the recommended sizes.     

```

```{r, eval=FALSE, include=TRUE}
%mktex(2 3 3 4 3 3 3 4 4, n=144, seed=2624)
     Design    Row,Col  D-Efficiency  D-Efficiency  Notes                                    
     ----------------------------------------------------------                              
          1      Start      100.0000      100.0000  Tab                                      
          1        End      100.0000
```


```{r, eval=FALSE, include=TRUE}
%mktblock(data=Randomized, nblocks=10, seed=2624) # 10 decks
/* 10 decks, 4 decks with 15 vignettes and 6 decks with 14 vignettes  */

%mktblock(data=Randomized, nblocks=15, seed=2624) # 15 decks
/* 15 decks, 9 decks with 10 vignettes and 6 decks with 9 vignettes  */
```


# Generation of the vignettes

- First we load the file containing the vignette information generated in SAS.

```{r,warning=FALSE,message=F}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(readxl,dplyr,knitr,kableExtra)

# df_vig <- xlsx::read.xlsx(file = "../input/vignetas.xlsx",sheetIndex = 1)
df_vig <- xlsx::read.xlsx(file = "input/vignetas15.xlsx",sheetIndex = 1)

colnames = c("obs","deck","vig","gender", "age", "migration", "religion", "education", "employment_status", "income", "political_orientation", "cultural_values")
names(df_vig) <- colnames
names(df_vig)
vig_dat<- df_vig %>% mutate(deck_vig=paste0(deck,vig)) %>% select(obs,deck,vig,deck_vig,everything())
```
- Save the vignette information for later use in the analysis.

```{r,warning=FALSE}
save(vig_dat,file = here::here("input/data/proc/vig_dim.RData"))
```


# ENG

Person [ID] is [Gender] and [Age] years old. [She/he] was born in [Migration Background] an is [Religion]. Person [ID] has completed [Education], is [Employment Status] and has a monthly income of [Income] at [her/his] disposal. [She/he] sees [herself/himself] politically [Political Orientation]. To person [ID], it is important to [Value Orientation].

```{r ENG,warning=FALSE,message=F}
df_vig_EN <- 
df_vig %>% 
    mutate(
      letter = recode(
        vig,
        `1` = "A",
        `2` = "B",
        `3` = "C",
        `4` = "D",
        `5` = "E",
        `6` = "F",
        `7` = "G",
        `8` = "H",
        `9` = "I",
        `10` = "J",        
      ),
      gender = recode(gender, `1` = "man", `2` = "woman"),
      age = recode(
        age,
        `1` = "25 years old.",
        `2` = "45 years old.",
        `3` = "65 years old."
      ),
      migration  = recode(
        migration,
        `1` = "Germany, has German parents",
        `2` = "Germany, has Turkish parents",
        `3` = "Syria, came to Germany"
      ),
      religion = recode(
        religion,
        `1` = "a devout Christian.",
        `2` = "a devout Muslim",
        `3` = "a devout Jew.",
        `4` = "not religious."
      ),
      education  = recode(
        education,
        `1` = "did an apprenticeship after finishing secondary school,",
        `2` = "has completed vocational training after finishing secondary school,",
        `3` = "has studied at university after graduating from high school,",
      ),
      income = recode(
        income,
        `1` = "850€",
        `2` = "2,500€",
        `3` = "6,000€",
      ),
      employment_status = recode(
        employment_status,
        `1` = "employed full-time",
        `2` = "unemployed",
        `3` = "a homemaker"
      ),
      political_orientation = recode(
        political_orientation,
        `1` = "standing on the left.",
        `2` = "standing in the middle.",
        `3` = "standing on the right.",
        `4` = "as uninterested."
      ),
      cultural_values = recode(
        cultural_values,
        `1` = "being tolerant and to help people around.",
        `2` = "feel safe, to fit in with others and to respect traditions.",
        `3` = "reach personal achievements and to be in charge.",
        `4` = "make your own decisions and lead an entertaining and adventurous life."
      )      
    )

table(df_vig_EN$education)
table(df_vig_EN$migration=="Syria,came to Germany" & df_vig_EN$education =="has completed vocational training after finishing secondary school,")

df_vig_EN$education <-
  ifelse(
    df_vig_EN$migration == "Syria,came to Germany" &
      df_vig_EN$education == "has completed vocational training after finishing secondary school,",
    yes = "qualified vocational training,",
    df_vig_EN$education
  )
table(df_vig_EN$education)

df_vig_EN$education <-
  ifelse(
    df_vig_EN$migration=="Syria,came to Germany" & 
      df_vig_EN$education =="has studied at university after graduating from high school,",
    yes = "a university degree course,",
    df_vig_EN$education
  )

table(df_vig_EN$education)

df_vig_EN$he_she <- ifelse(df_vig_EN$gender=="man",yes = "He",no = "She")
df_vig_EN$himself_herself <- ifelse(df_vig_EN$gender=="man",yes = "himself",no = "herself")
df_vig_EN$his_her <- ifelse(df_vig_EN$gender=="man",yes = "his",no = "her")



# sjmisc::flat_table(table(df_vig_EN$income,df_vig_EN$employment_status))
# df_vig_EN %>% select(gender:cultural_values) %>% polycor::hetcor()

df_vig_EN %>% group_by(deck) %>% 
  summarise(vig=n()) %>% 
  kable(col.names = c("Deck","Number of vignettes")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r text-ENG}
"Person [ID] is [Gender] and [Age] years old. [She/he] was born in [Migration Background] an is [Religion]. Person [ID] has completed [Education], is [Employment Status] and has a monthly income of [Income] at [her/his] disposal. [She/he] sees [herself/himself] politically [Political Orientation]. To person [ID], it is important to [Value Orientation]."

df_vig_EN$vig_text_EN <- 
paste("Person",df_vig_EN$letter,"is a",df_vig_EN$gender,"and is",df_vig_EN$age,df_vig_EN$he_she,"was born in",df_vig_EN$migration,"and is",df_vig_EN$religion,
      "Person",df_vig_EN$letter,df_vig_EN$education,"is",df_vig_EN$employment_status,"and has a monthly income of",df_vig_EN$income,"at",df_vig_EN$his_her,"disposal.",
      df_vig_EN$he_she,"sees",df_vig_EN$himself_herself,"politically",df_vig_EN$political_orientation,
      "To person",df_vig_EN$letter,"it is important to",df_vig_EN$cultural_values)
```


# DEU

Person [ID] ist [Geschlecht] und [Alter] Jahre alt. Sie ist in [Migrationshintergrund] und ist [Religion (+Geschlecht)]. Person [ID] hat [Bildung + (Migrationshintergrund)] absolviert, ist [Erwerbsstatus (+Geschlecht)] und verfügt über ein monatliches Einkommen von [Einkommen]. Sie versteht sich selbst als politisch [Polititische Orientierung]. Es ist Person [ID] wichtig, [Wertorientierung].

```{r DEU,warning=FALSE,message=F}
df_vig_DE <- 
df_vig %>% 
    mutate(
      letter = recode(
        vig,
        `1` = "A",
        `2` = "B",
        `3` = "C",
        `4` = "D",
        `5` = "E",
        `6` = "F",
        `7` = "G",
        `8` = "H",
        `9` = "I",
        `10` = "J",        
      ),
      gender = recode(gender, `1` = "männlich", `2` = "weiblich"),
      age = recode(
        age,
        `1` = "25",
        `2` = "45",
        `3` = "65"
      ),
      migration  = recode(
        migration,
        `1` = "Deutschland geboren, hat deutsche Eltern",
        `2` = "Deutschland geboren, hat türkische Eltern",
        `3` = "Syrien geboren, nach Deutschland gekommen"
      ),
      religion = recode(
        religion,
        `1` = "gläubiger Christ.",
        `2` = "gläubiger Muslim.",
        `3` = "gläubiger Jude.",
        `4` = "nicht religiös."
      ),
      education  = recode(
        education,
        `1` = "nach dem Hauptschulabschluss eine Lehre",
        `2` = "nach dem Realschulabschluss eine Berufsausbildung",
        `3` = "nach dem Abitur ein Studium",
      ),
      income = recode(
        income,
        `1` = "850€.",
        `2` = "2,500€.",
        `3` = "6,000€.",
      ),
      employment_status = recode(
        employment_status,
        `1` = "erwerbstätig",
        `2` = "arbeitslos",
        `3` = "Hausmann"
      ),
      political_orientation = recode(
        political_orientation,
        `1` = "linksstehend.",
        `2` = "in der Mitte stehend.",
        `3` = "rechtsstehend.",
        `4` = "uninteressiert."
      ),
      cultural_values = recode(
        cultural_values,
        `1` = "tolerant zu sein und den Menschen in ihrer Umgebung zu helfen.",
        `2` = "sich sicher zu fühlen, sich anderen anzupassen und Traditionen zu respektieren.",
        `3` = "persönliche Erfolge zu erzielen und das Sagen zu haben.",
        `4` = "eigene Entscheidungen zu treffen und ein unterhaltsames und abenteuerliches Leben zu führen."
      )      
    )

"nach dem Hauptschulabschluss eine Lehre,"
"nach dem Realschulabschluss eine Berufsausbildung,"
"nach dem Abitur ein Studium,"

table(df_vig_DE$education)
table(df_vig_DE$migration=="Syrien geboren, nach Deutschland gekommen" & 
        df_vig_DE$education =="nach dem Hauptschulabschluss eine Lehre")

table(df_vig_DE$migration=="Syrien geboren, nach Deutschland gekommen" & 
        df_vig_DE$education =="nach dem Realschulabschluss eine Berufsausbildung")

table(df_vig_DE$migration=="Syrien geboren, nach Deutschland gekommen" & 
        df_vig_DE$education =="nach dem Abitur ein Studium")

df_vig_DE$education <-
  ifelse(
    df_vig_DE$migration=="Syrien geboren, nach Deutschland gekommen" &
      df_vig_DE$education =="nach dem Hauptschulabschluss eine Lehre",
    yes = "eine einfache Berufsausbildung", #level low
     df_vig_DE$education
  )

df_vig_DE$education <-
  ifelse(
    df_vig_DE$migration=="Syrien geboren, nach Deutschland gekommen" &
      df_vig_DE$education =="nach dem Realschulabschluss eine Berufsausbildung",
    yes = "eine qualifizierte Berufsausbildung", #level middle
    df_vig_DE$education
  )
df_vig_DE$education <-
  ifelse(
    df_vig_DE$migration=="Syrien geboren, nach Deutschland gekommen" &
      df_vig_DE$education =="nach dem Abitur ein Studium",
    yes = "ein Hochschulstudium,", #level high
    df_vig_DE$education
  )

"gläubiger Christ."
"gläubiger Muslim."
"gläubiger Jude."
"nicht religiös."

table(df_vig_DE$religion)
table(df_vig_DE$gender=="weiblich" & 
        df_vig_DE$religion =="gläubiger Christ.")

table(df_vig_DE$gender=="weiblich" & 
        df_vig_DE$religion =="gläubiger Muslim.")

table(df_vig_DE$gender=="weiblich" & 
        df_vig_DE$religion =="gläubiger Jude.")

table(df_vig_DE$gender=="weiblich" & 
        df_vig_DE$religion =="nicht religiös.")

df_vig_DE$religion <-
  ifelse(
    df_vig_DE$gender=="weiblich" & df_vig_DE$religion =="gläubiger Christ.",
    yes = "gläubige Christin.", #Woman-Christian
     df_vig_DE$religion
  )

df_vig_DE$religion <-
  ifelse(
    df_vig_DE$gender=="weiblich" & df_vig_DE$religion =="gläubiger Muslim.",
    yes = "gläubige Muslima.", #woman-Muslim
     df_vig_DE$religion
  )

df_vig_DE$religion <-
  ifelse(
    df_vig_DE$gender=="weiblich" & df_vig_DE$religion =="gläubiger Jude.",
    yes = "gläubige Jüdin.", #woman-Muslim
     df_vig_DE$religion
  )

sjmisc::frq(df_vig_DE$religion)

table(df_vig_DE$gender=="weiblich" & 
        df_vig_DE$employment_status =="Hausmann")

df_vig_DE$employment_status <-
  ifelse(
    df_vig_DE$gender=="weiblich" & df_vig_DE$employment_status =="Hausmann",
    yes = "Hausfrau", #woman-Houselabour
     df_vig_DE$employment_status
  )
sjmisc::frq(df_vig_DE$employment_status)
```

```{r}
"Person [ID] ist [Geschlecht] und [Alter] Jahre alt. Sie ist in [Migrationshintergrund] und ist [Religion (+Geschlecht)]. Person [ID] hat [Bildung + (Migrationshintergrund)] absolviert, ist [Erwerbsstatus (+Geschlecht)] und verfügt über ein monatliches Einkommen von [Einkommen]. Sie versteht sich selbst als politisch [Polititische Orientierung]. Es ist Person [ID] wichtig, [Wertorientierung]."

df_vig_DE$vig_text_DE <-
  paste("Person",df_vig_DE$letter,"ist",df_vig_DE$gender,"und",df_vig_DE$age,"Sie ist in",df_vig_DE$migration,"und ist",df_vig_DE$religion,
      "Person",df_vig_DE$letter,"hat",df_vig_DE$education,"absolviert, ist",df_vig_DE$employment_status,"und verfügt über ein monatliches Einkommen von",
      df_vig_DE$income,"Sie versteht sich selbst als politisch",df_vig_DE$political_orientation,
      "Es ist Person",df_vig_DE$letter,"wichtig",df_vig_DE$cultural_values)
```

# ESP
```{r ESP,warning=FALSE,message=F}
df_vig_ESP <- 
df_vig %>% 
    mutate(
      letter = recode(
        vig,
        `1` = "A",
        `2` = "B",
        `3` = "C",
        `4` = "D",
        `5` = "E",
        `6` = "F",
        `7` = "G",
        `8` = "H",
        `9` = "I",
        `10` = "J",        
      ),
      gender = recode(gender, `1` = "hombre", `2` = "mujer"),
      age = recode(
        age,
        `1` = "25 años.",
        `2` = "45 años.",
        `3` = "65 años."
      ),
      migration  = recode(
        migration,
        `1` = "Chile, tiene padres Chilenos",
        `2` = "Chile, tiene padres Peruanos",
        `3` = "Venezuela, vino a Chile"
      ),
      religion = recode(
        religion,
        `1` = "es católico.",
        `2` = "es evangélico.",
        `3` = "es judío.",
        `4` = "no es religioso."
      ),
      education  = recode(
        education,
        `1` = "terminó la Educación Básica,",
        `2` = "terminó la Educación Media,",
        `3` = "fue a la universidad y obtuvo un título universitario,",
      ),
      income = recode(
        income,
        `1` = "$500.000",
        `2` = "$910.000",
        `3` = "$4.100.000",
      ),
      employment_status = recode(
        employment_status,
        `1` = "empleado tiempo completo",
        `2` = "desempleado",
        `3` = "dueño de casa"
      ),
      political_orientation = recode(
        political_orientation,
        `1` = "de izquierda.",
        `2` = "de centro.",
        `3` = "de derecha.",
        `4` = "desinteresado."
      ),
      cultural_values = recode(
        cultural_values,
        `1` = "ser tolerante y ayudar a la gente que te rodea.",
        `2` = "sentirse seguro, adaptarse a los demás y respetar las tradiciones.",
        `3` = "alcanzar el éxito personal y estar al mando.",
        `4` = "tomar sus propias decisiones y llevar una vida divertida y llena de aventuras"
      )      
    )

# df_vig_EN$education <-
#   ifelse(
#     df_vig_EN$migration == "Syria,came to Germany" &
#       df_vig_EN$education == "has completed vocational training after finishing secondary school,",
#     yes = "qualified vocational training,",
#     df_vig_EN$education
#   )
# table(df_vig_EN$education)
# 
# df_vig_EN$education <-
#   ifelse(
#     df_vig_EN$migration=="Syria,came to Germany" & 
#       df_vig_EN$education =="has studied at university after graduating from high school,",
#     yes = "a university degree course,",
#     df_vig_EN$education
#   )
# 
# table(df_vig_EN$education)

df_vig_ESP$employment_status <-
  ifelse(
    df_vig_ESP$employment_status=="dueño de casa" &
    df_vig_ESP$gender=="mujer",
    yes = "dueña de casa",
    df_vig_ESP$employment_status
  )

df_vig_ESP$employment_status <-
  ifelse(
    df_vig_ESP$employment_status=="empleado tiempo completo" &
    df_vig_ESP$gender=="mujer",
    yes = "empleada tiempo completo",
    df_vig_ESP$employment_status
  )

df_vig_ESP$employment_status <-
  ifelse(
    df_vig_ESP$employment_status=="desempleado" &
    df_vig_ESP$gender=="mujer",
    yes = "desempleada",
    df_vig_ESP$employment_status
  )


df_vig_ESP$religion <-
  ifelse(df_vig_ESP$religion == "es católico." & df_vig_ESP$gender=="mujer",
    yes = "es católica.",
    df_vig_ESP$religion
  )

df_vig_ESP$religion <-
  ifelse(df_vig_ESP$religion == "es evangélico." & df_vig_ESP$gender=="mujer",
    yes = "es evangélica.",
    df_vig_ESP$religion
  )

df_vig_ESP$religion <-
  ifelse(df_vig_ESP$religion == "es judío." & df_vig_ESP$gender=="mujer",
    yes = "es judía.",
    df_vig_ESP$religion
  )

df_vig_ESP$religion <-
  ifelse(df_vig_ESP$religion == "no es religioso." & df_vig_ESP$gender=="mujer",
    yes = "no es religiosa.",
    df_vig_ESP$religion
  )

df_vig_ESP$religion <-
  ifelse(df_vig_ESP$religion == "es evangélico." & df_vig_ESP$gender=="mujer",
    yes = "es evangélica.",
    df_vig_ESP$religion
  )

df_vig_ESP$religion <-
  ifelse(df_vig_ESP$religion == "es judío." & df_vig_ESP$gender=="mujer",
    yes = "es judía.",
    df_vig_ESP$religion
  )


df_vig_ESP$cultural_values <-
  ifelse(df_vig_ESP$cultural_values == "sentirse seguro, adaptarse a los demás y respetar las tradiciones." & df_vig_ESP$gender=="mujer",
    yes = "sentirse segura, adaptarse a los demás y respetar las tradiciones.",
    df_vig_ESP$cultural_values
  )

df_vig_ESP$es_esta <-
  ifelse(
    df_vig_ESP$employment_status %in% c("dueño de casa","dueña de casa"),
    yes = "es",
    no = "está"
  )

# sjmisc::flat_table(table(df_vig_EN$income,df_vig_EN$employment_status))
# df_vig_EN %>% select(gender:cultural_values) %>% polycor::hetcor()

```

```{r text-ESP}
df_vig_ESP$vig_text_ESP <- 
paste("La Persona",df_vig_ESP$letter,"es",df_vig_ESP$gender,"y tiene",df_vig_ESP$age,df_vig_ESP$he_she,"Nació en",df_vig_ESP$migration,"y",df_vig_ESP$religion,
      "La Persona",df_vig_ESP$letter,df_vig_ESP$education,df_vig_ESP$es_esta,df_vig_ESP$employment_status,"y tiene unos ingresos mensuales de",df_vig_ESP$income,"a","su","disposición.",
      df_vig_ESP$he_she,df_vig_ESP$himself_herself,"Se considera políticamente",df_vig_ESP$political_orientation,
      "Para la persona",df_vig_ESP$letter,"es importante",df_vig_ESP$cultural_values)
head(df_vig_ESP$vig_text_ESP,10) %>%
  kable(format = "html") %>%
  kable_styling()

```

- Imagina que conoces a la persona [ID] a través de tu círculo de conocidos. ¿Qué probabilidad hay de que te lleves bien con la persona [ID]?
- Imagina que te enfrentas a una tarea que no puedes realizar por ti mismo. ¿Con qué probabilidad pedirías ayuda a la persona [ID]?
- Imagina que la persona [ID] se muda a tu barrio. ¿Qué probabilidad hay de que entres en conflicto con esa persona?

Test link: https://kunden.infas-online.de/q1/SurveyServlet 


*Introduction*

En la siguiente sección nos interesa conocer su opinión sobre cómo la gente se encuentra con personas diferentes en situaciones cotidianas. Necesitamos su ayuda para averiguarlo. Se le presentarán descripciones de personas con distintas características como en el siguiente ejemplo:
- La Persona B es hombre y tiene 25 años. Nació en Chile, tiene padres Chilenos y es católico. La Persona B terminó la Educación Básica, está empleado tiempo completo y tiene unos ingresos mensuales de $250.000 a su disposición. Se considera políticamente desinteresado. Para la persona B es importante sentirse seguro, adaptarse a los demás y respetar las tradiciones.
Luego de la presentación de cada descripción, se preguntan tres cosas: 
- Imagina que conoces a la persona B a través de tu círculo de conocidos. ¿Qué probabilidad hay de que te lleves bien con la persona B?"
- Imagina que te enfrentas a una tarea que no puedes realizar por ti mismo. ¿Con qué probabilidad pedirías ayuda a la persona B?"
- Imagina que la persona B se muda a tu barrio. ¿Qué probabilidad hay de que entres en conflicto con esa persona?
Le describiremos 10 personas y usted nos dirá cómo se encontraría con esas personas en la vida cotidiana. Por favor, responda espontáneamente a lo que se le ocurra en el primer momento.
Esto no es ningún tipo de prueba de conocimiento. Solo nos interesa conocer sus opiniones, por lo que no hay respuestas correctas o incorrectas. 


```{r}
# Template string
df_vig_ESP$p01 <- "Imagina que conoces a la persona {ID} a través de tu círculo de conocidos. ¿Qué probabilidad hay de que te lleves bien con la persona {ID}?"
df_vig_ESP$p02 <- "Imagina que te enfrentas a una tarea que no puedes realizar por ti mismo. ¿Con qué probabilidad pedirías ayuda a la persona {ID}?"
df_vig_ESP$p03 <- "Imagina que la persona {ID} se muda a tu barrio. ¿Qué probabilidad hay de que entres en conflicto con esa persona?"

df_vig_ESP$p01 <- stringi::stri_replace_all(str = df_vig_ESP$p01,regex = "\\{ID\\}",replacement = df_vig_ESP$letter)
df_vig_ESP$p02 <- stringi::stri_replace_all(str = df_vig_ESP$p02,regex = "\\{ID\\}",replacement = df_vig_ESP$letter)
df_vig_ESP$p03 <- stringi::stri_replace_all(str = df_vig_ESP$p03,regex = "\\{ID\\}",replacement = df_vig_ESP$letter)

vignetas <- df_vig_ESP %>% 
  mutate(type="note",
         name=paste0("deck",deck,"vig",vig),
         showif=paste0("ran_group == ",deck),
         optional=NA,
         # vig_text_ESP=paste0("[",name,"]",vig_text_ESP)
         ) %>% 
  select(deck,vig,type,optional,name,showif,label=vig_text_ESP,block_order=letter)


p01 <- df_vig_ESP %>% select(deck,vig,label=p01,block_order=letter) %>% 
  mutate(name=paste0("d",deck,"v",vig,"_p01"),
         choice1="Nada<br>probable",choice2="Muy<br>probable",
         type="range_ticks 0,10,1",
         showif=paste0("ran_group == ",deck),optional=" "
         # label=paste0("[",name,"] ",label)
         ) %>% 
  select(deck,vig,type,name,showif,label,choice1,choice2,block_order)

p02 <- df_vig_ESP %>% select(deck,vig,label=p02,block_order=letter)%>% 
  mutate(name=paste0("d",deck,"v",vig,"_p02"),
         choice1="Nada<br>probable",choice2="Muy<br>probable",
         type="range_ticks 0,10,1",
         showif=paste0("ran_group == ",deck),optional=" "
         # label=paste0("[",name,"] ",label)
         ) %>% 
  select(deck,vig,type,name,showif,label,choice1,choice2,block_order)
p03 <- df_vig_ESP %>% select(deck,vig,label=p03,block_order=letter)%>% 
  mutate(name=paste0("d",deck,"v",vig,"_p03"),
         choice1="Nada<br>probable",choice2="Muy<br>probable",
         type="range_ticks 0,10,1",
         showif=paste0("ran_group == ",deck),optional=" "
         # label=paste0("[",name,"] ",label)         
         ) %>% 
  select(deck,vig,type,name,showif,label,choice1,choice2,block_order)

submit <- df_vig_ESP %>% 
  mutate(type="submit",label="Siguiente",name=paste0("d",deck,"v",vig,"submit"),block_order=letter,showif=paste0("ran_group == ",deck)) %>% 
  select(deck,vig,type,label,name,showif,block_order) 
# %>% 
#   filter(vig %in% c(3,6,9)) 

template_formr <- 
  bind_rows(vignetas,p01,p02,p03,submit) %>% 
  arrange(deck,vig) %>% 
  mutate(item_order="") %>% 
  select(deck,vig,type,optional,name,showif,label,choice1,choice2,block_order,item_order) %>% 
  add_row(.before = 1,type = "random 1,15",name = "ran_group")
# template_formr$item_order <- template_formr$vig  
# template_formr$block_order <-  toupper(sapply(template_formr$deck, function(i) letters[i]))
# 
# template_formr$showif <- NA

# template_formr$showif <- stringi::stri_replace_all(str = template_formr$showif,replacement = "")
# 
# template_formr$showif <- "shuffle$group == 15" 

template_formr %>% 
  xlsx::write.xlsx(file = "output/formr_vignetas_ESP.xlsx",row.names = F,showNA = F)
```


# Save vignetes

```{r}
# df_vig_DE %>% 
#   xlsx::write.xlsx(file = "output/vignettes_DE.xlsx",row.names = F)
# 
# df_vig_EN %>% 
#   xlsx::write.xlsx(file = "output/vignettes_EN.xlsx",row.names = F)

df_vig_ESP %>% 
  xlsx::write.xlsx(file = "output/vignettes_ESP.xlsx",row.names = F)
```



```{r eval=FALSE, include=FALSE}
# devtools::install_github("zumbov2/deeplr")
# my_key <- "8aa9d9db-f3bd-fe6e-089e-8e16786ad7ab:fx"
# 
# langs <- deeplr::available_languages2(my_key)
# 
# df_vig$vig_text_noname_DE <- df_vig$vig_text_noname
# 
# df_vig$vig_text_noname_DE <-
# deeplr::translate2(
#   text = df_vig$vig_text_noname,
#   target_lang = "DE",
#   auth_key = my_key
#   )
```


