---
title: "Data Preparation"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output: 
  html_document: 
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
      number_sections: yes
    code_folding: show  
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE 
                      )
options(scipen=9999) # desactivar notacion cientifica

set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1) 
options(ggplot2.discrete.colour = set1) 
ggplot2::theme_set(ggplot2::theme_bw()) 
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
```

# Models: Trust

1)	Imagine you know person [ID] through your circle of acquaintances. How likely is it that you would get along with person [ID]? 

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1) 
options(ggplot2.discrete.colour = set1) 
ggplot2::theme_set(ggplot2::theme_bw()) 
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))
options(scipen=999)
library(estimatr)
library(plm)
library(lme4)
library(sjmisc)
library(texreg)
library(car)
library(dplyr)

load(file = here::here("input/data/proc/df_vig_CL.Rdata"))
df_vig<- df_vig_CL;
df_vig$friendship_z <- scale(df_vig$friendship)

df_vig$income_dec<- dplyr::ntile(df_vig$income_eq,10)

df_vig %>% 
  group_by(income_dec) %>% 
  summarise(ingreso=mean(income_eq,na.rm = T),
            median=median(income_eq,na.rm = T),
            min=min(income_eq,na.rm = T),
            max=max(income_eq,na.rm = T)) %>% knitr::kable()


df_vig$topmibot <- car::recode(df_vig$income_dec,"10=3; 5:9=2;1:4=1")
frq(df_vig$topmibot)

#Información real de casen:
# | Decil | Promedio ingreso | Mediana    | Mínimo   | Máximo       |
# |------:|-----------------:|-----------:|---------:|-------------:|
# | 1     | 74.215,77        | 62.500     | 0        | 197.000      |
# | 2     | 287.536,19       | 300.000    | 197.000  | 382.500      |
# | 3     | 431.877,79       | 422.000    | 382.500  | 500.000      |
# | 4     | 559.853,27       | 560.000    | 500.000  | 630.000      |
# | 5     | 718.346,29       | 710.833    | 630.000  | 800.000      |
# | 6     | 886.331,68       | 890.000    | 800.000  | 990.000      |
# | 7     | 1.091.815,41     | 1.090.000  | 990.000  | 1.212.083    |
# | 8     | 1.384.631,47     | 1.382.500  | 1.212.083| 1.580.000    |
# | 9     | 1.879.174,81     | 1.856.250  | 1.580.000| 2.282.833    |
# | 10    | 4.009.911,34     | 3.200.000  | 2.282.833| 76.500.000   |

# Clasificación en deciles según los rangos dados:
df_vig$decil_autoh <- car::recode(df_vig$income_eq,
  "0:197000=1;
   197001:382500=2;
   382501:500000=3;
   500001:630000=4;
   630001:800000=5;
   800001:990000=6;
   990001:1212083=7;
   1212084:1580000=8;
   1580001:2282833=9;
   2282834:99999999=10",
  as.factor = FALSE
)
df_vig$quintil_autoh <- car::recode(df_vig$decil_autoh,"1:2=1;3:4=2;5:6=3;7:8=4;9:10=5")

# Predominand human value according to the highest value
df_vig$humanvalue <- apply(df_vig[, c("self_transcendence", "self_enhancement", "openness_change", "conservation")], 1, function(x) {
  names(x)[which.max(x)]
})

df_vig$humanvalue <- factor(df_vig$humanvalue,levels = c("self_enhancement","openness_change","conservation","self_transcendence"))

levels(df_vig$religion)
# Recode
df_vig$religions <- car::recode(
  df_vig$religion,
  "'Evangelical'='Evangelical';
   'Evangelicals'='Evangelical';   
   'Protestant'='Evangelical';
   'Atheist'='Non-religious';
   'Agnostic'='Non-religious';
   'None'='Non-religious'")

df_vig$religions <- relevel(x = df_vig$religions,ref = "Non-religious")

# Inspect the result
table(df_vig$religion,df_vig$religions)
frq(df_vig$religions)

df_vig$neighborhoodr<- sjmisc::rec(df_vig$neighborhood,rec = "rev")  

respondentsN <- unique(df_vig$pid);length(respondentsN)

drop_analysis <- df_vig

df_vig <- df_vig %>% group_by(pid) %>% mutate(n_obs=n()) %>% 
  select(pid,deck,deck_vig,friendship,friendship_z,vincome,vedu,norelig,vmigback,polcenter,selftrans,vgender,vage,vempstat,
                  income_qui,educat,migration,religions,ideology_collapsed,humanvalue,female,age_group,n_obs,timemin,timesec,deck) %>% na.omit()
respondentsN2 <- unique(df_vig$pid);length(respondentsN2)
df_vig2 <- 
df_vig %>% select(pid,deck,friendship_z,vincome,vedu,norelig,vmigback,polcenter,selftrans,vgender,vage,vempstat,
                  income_qui,educat,migration,religions,ideology_collapsed,humanvalue,female,age_group,n_obs,timemin,timesec) %>% na.omit()

df_vig2 <- df_vig2 %>% group_by(pid) %>% mutate(n_obs_lw=n())

df_vig2 <- df_vig2 %>% filter(n_obs_lw>=6)

summary(df_vig$timemin)
summary(df_vig$timesec)

# Create the missingness indicator in the full sample
drop_analysis <- drop_analysis |>
  mutate(dropped = ifelse(pid %in% df_vig$pid, 0, 1)) %>% 
  select(pid,income_qui,educat,migration,religions,ideology_collapsed,female,age_group,dropped) %>%  
  group_by(pid) |>
  slice(1) |>
  ungroup()

table(drop_analysis$dropped)
summary(drop_analysis)

# Logistic regression of dropping on respondent characteristics
model_missing <- glm(
  dropped ~ factor(income_qui) + educat + migration + religions +  female + age_group,
  data   = drop_analysis,
  family = binomial(link = "logit")
)
summary(model_missing)
library(performance)
r2_mcfadden(model_missing)

# Main effects-----------------------------------------------------------------

lm_fship_vig_null   <- lmer(friendship_z~(1|pid),data = df_vig)

lm_fship_vig_resp   <- lmer(friendship_z~
                            vincome+vedu+
                              norelig+vmigback+
                              polcenter+selftrans+
                              vgender+vage+vempstat+
                              factor(income_qui)+educat+
                              migration+religions+
                              ideology_collapsed+humanvalue+female+age_group+
                              # factor(deck)+scale(timemin)+
                              (1|pid),data = df_vig)

# Including time does not affect the results
# Including deck does not affect the results

lm_fship_vig_resp_t   <- lmer(friendship_z~
                            vincome+vedu+
                              norelig+vmigback+
                              polcenter+selftrans+
                              vgender+vage+vempstat+
                              factor(income_qui)+educat+
                              migration+religions+
                              ideology_collapsed+humanvalue+female+age_group+scale(timemin)+
                              (1|pid),data = df_vig)


lm_fship_vig_resp2   <- lmer(friendship_z~
                            vincome+vedu+
                              norelig+vmigback+
                              polcenter+selftrans+
                              vgender+vage+vempstat+
                              factor(income_qui)+educat+
                              migration+religions+
                              ideology_collapsed+humanvalue+female+age_group+
                              (1|pid),data = df_vig2)

lm_fship_vig_resp2_t   <- lmer(friendship_z~
                            vincome+vedu+
                              norelig+vmigback+
                              polcenter+selftrans+
                              vgender+vage+vempstat+
                              factor(income_qui)+educat+
                              migration+religions+
                              ideology_collapsed+humanvalue+female+age_group+scale(timemin)+
                              (1|pid),data = df_vig2)

screenreg(list(lm_fship_vig_resp,lm_fship_vig_resp_t,lm_fship_vig_resp2,lm_fship_vig_resp2_t),digits = 3)

# lm_coop_vig_resp   <- lmer(cooperation~
#                             vincome+vedu+
#                               norelig+vmigback+
#                               polcenter+selftrans+
#                               vgender+vage+vempstat+
#                               factor(income_qui)+educat+
#                               migration+religions+
#                               ideology_collapsed+humanvalue+female+age_group+
#                               (1|pid),data = df_vig)
# 
# 
# lm_neigh_vig_resp   <- lmer(neighborhoodr~
#                             vincome+vedu+
#                               norelig+vmigback+
#                               polcenter+selftrans+
#                               vgender+vage+vempstat+
#                               factor(income_qui)+educat+
#                               migration+religions+
#                               ideology_collapsed+humanvalue+female+age_group+
#                               (1|pid),data = df_vig)
# 
# lm_coes_vig_resp   <- lmer(cohesion~
#                             vincome+vedu+
#                               norelig+vmigback+
#                               polcenter+selftrans+
#                               vgender+vage+vempstat+
#                               factor(income_qui)+educat+
#                               migration+religions+
#                               ideology_collapsed+humanvalue+female+age_group+
#                               (1|pid),data = df_vig)
# 
# lm_coes_vig_resp2   <- lmer(cohesion~
#                             vincome+vedu+
#                               norelig+vmigback+
#                               polcenter+selftrans+
#                               vgender+vage+vempstat+
#                               factor(income_qui)+educat+
#                               migration+religions+
#                               ideology_collapsed+humanvalue+female+age_group+
#                               (1|pid),data = df_vig2)
# 
# screenreg(list(lm_coes_vig_resp,lm_coes_vig_resp2))

library(performance)
# r2(lm_fship_vig_resp,verbose = T)
# r2(lm_fship_vig_resp2,verbose = T)

# avgcomp_fship_inco <- marginaleffects::avg_comparisons(lm_fship_vig_resp, variables = list(vincome="sequential"))
# avgcomp_fship_educ <- marginaleffects::avg_comparisons(lm_fship_vig_resp, variables = list(vedu="sequential"))


# Conditional R² tells you how well the entire model explains variation, including within-group differences.
# Marginal R² tells you how well your predictors explain variation between units.
# screenreg(list(lm_fship_vig_resp,lm_coop_vig_resp,lm_neigh_vig_resp,lm_coes_vig_resp))

# Cross-level interaction------------------------------------------------------

cl_trust_inco <- update(lm_fship_vig_resp,. ~ . +vincome*factor(income_qui) +(vincome|pid) -(1|pid))
cl_trust_educ <- update(lm_fship_vig_resp,. ~ . +vedu*educat +(vedu|pid) -(1|pid))
cl_trust_migr <- update(lm_fship_vig_resp,. ~ . +vmigback*migration +(vmigback|pid) -(1|pid))
cl_trust_reli <- update(lm_fship_vig_resp,. ~ . +norelig*religions +(norelig|pid) -(1|pid))
cl_trust_vals <- update(lm_fship_vig_resp,. ~ . +selftrans*humanvalue +(humanvalue|pid) -(1|pid))
cl_trust_poli <- update(lm_fship_vig_resp,. ~ . +polcenter*ideology_collapsed +(polcenter|pid) -(1|pid))

interactions_trust<- list(cl_trust_inco,cl_trust_educ,cl_trust_migr,cl_trust_reli,cl_trust_vals,cl_trust_poli)

screenreg(interactions_trust,digits = 3)
```

```{r tableS01}
htmlreg(
  lm_fship_vig_resp,
  single.row = T,
  digits = 3,
  file = here::here("output/tables/table0002.html"),
  caption = "Table : Multilevel Model of Getting along based on vignette and respondent characteristics",
  caption.above = TRUE,
  custom.coef.map = list(
    # Vignette level — plain (primary)
    "vincomeMiddle"                         = "$910.000",
    "vincomeHigh"                           = "$4.000.000",
    "veduMiddle"                            = "High school",
    "veduHigh"                              = "Universitary",
    "noreligCatholic"                       = "Catholic",
    "noreligEvangelical"                    = "Evangelical",
    "noreligJewish"                         = "Jewish",
    "vmigback2nd generation (Peruvian)"     = "Peruvian",
    "vmigback1. Generation (Venezuelan)"    = "Venezuelan",
    "polcenterLeft-wing"                    = "Left-wing",
    "polcenterRight-wing"                   = "Right-wing",
    "polcenterUninterested"                 = "Uninterested",
    "selftransConservation"                 = "Conservation",
    "selftransOpeness to change"            = "Openness to Change",
    "selftransSelf-transcendence"           = "Self-transcendence",
    "vgenderFemale"                         = "Female",
    "vage45 years"                          = "45 years",
    "vage65 years"                          = "65 years",
    "vempstatUnemployed"                    = "Unemployed",
    "vempstatHomemaker"                     = "Homemaker",
    # Respondent level — dashed prefix (secondary)
    "factor(income_qui)2"                   = "— Income Quintile 2",
    "factor(income_qui)3"                   = "— Income Quintile 3",
    "factor(income_qui)4"                   = "— Income Quintile 4",
    "factor(income_qui)5"                   = "— Income Quintile 5",
    "educatSecondary"                       = "— Secondary",
    "educatTechnical"                       = "— Technical",
    "educatUniversitary"                    = "— University",
    "migrationVenezuela"                    = "— Venezuela",
    "migrationPeru"                         = "— Peru",
    "migrationBolivia"                      = "— Bolivia",
    "migrationOthers"                       = "— Others",
    "religionsBeliever without affiliation" = "— Believer w/o Affiliation",
    "religionsCatholic"                     = "— Catholic",
    "religionsEvangelical"                  = "— Evangelical",
    "religionsJewish"                       = "— Jewish",
    "religionsPrefer not to answer"         = "— Prefer not to answer",
    "ideology_collapsedCenter"              = "— Center",
    "ideology_collapsedRight"               = "— Right",
    "ideology_collapsedNon-Partisan"        = "— Non-Partisan",
    "humanvalueopenness_change"             = "— Openness to Change",
    "humanvalueconservation"                = "— Conservation",
    "humanvalueself_transcendence"          = "— Self-transcendence",
    "female"                                = "— Female",
    "age_group25-34"                        = "— 25–34",
    "age_group35-44"                        = "— 35–44",
    "age_group45-54"                        = "— 45–54",
    "age_group55-64"                        = "— 55–64",
    "age_group65-74"                        = "— 65–74",
    "age_group75-84"                        = "— 75–84",
    "age_group85+"                          = "— 85+",
    "(Intercept)"                           = "Intercept"
  ),
  groups = list(
    "Income (ref.=$500.000)"                  = 1:2,
    "Education (ref.=Primary)"                = 3:4,
    "Religion (ref.=No religious)"            = 5:7,
    "Migration (ref.=Chilean)"                = 8:9,
    "Politics (ref.=Center)"                  = 10:12,
    "Human Values (ref.=Self-enhancement)"    = 13:15,
    "Gender (ref.=Male)"                      = 16:16,
    "Age (ref.=25 years)"                     = 17:18,
    "Employment (ref.=Employed)"              = 19:20,
    "Rs: Income (ref.=Quintile 1)"            = 21:24,
    "Rs: Education (ref.=Primary)"            = 25:27,
    "Rs: Migration (ref.=Chilean)"            = 28:31,
    "Rs: Religion (ref.=Atheist/Agnostic)"    = 32:36,
    "Rs: Ideology (ref.=Left)"                = 37:39,
    "Rs: Human Values (ref.=Self-enhancement)"= 40:42,
    "Rs: Gender (ref.=Male)"                  = 43:43,
    "Rs: Age Group (ref.=18–24)"              = 44:50
  ),
  include.aic    = FALSE,
  include.loglik = FALSE,
  custom.gof.names = c(
    "BIC",
    "Num. Vignettes",
    "Num. Respondents",
    "Var: Respondent (Intercept)",
    "Var: Vignettes"
  ),
  custom.note = "Note: Coefficients are presented with standard errors in parentheses.<br>
  Coefficients are standardized <br>
  Rs = Respondent. %stars"
)
```

```{r}
interactions <- list(cl_trust_inco,cl_trust_educ,cl_trust_migr,cl_trust_reli,cl_trust_vals,cl_trust_poli)

htmlreg(
  interactions[1:2],
  single.row = T,
  digits = 3,
  file = here::here("output/tables/tableS002a.html"),
  caption = "Table S2a: Multilevel regression models with cross-level interactions vignette income and education",
  caption.above = TRUE,
  custom.model.names = c(
    "M1: Income",
    "M2: Education"
  ),
  custom.coef.map = list(
    # Intercept
    "(Intercept)"                            = "Intercept",
    # Vignette Income
    "vincomeMiddle"                          = "$910.000",
    "vincomeHigh"                            = "$4.000.000",
    # Vignette Education
    "veduMiddle"                             = "High school",
    "veduHigh"                               = "Universitary",
    # Respondent Income
    "factor(income_qui)2"                    = "— Quintile 2",
    "factor(income_qui)3"                    = "— Quintile 3",
    "factor(income_qui)4"                    = "— Quintile 4",
    "factor(income_qui)5"                    = "— Quintile 5",
    # Respondent Education
    "educatSecondary"                        = "— Secondary",
    "educatTechnical"                        = "— Technical",
    "educatUniversitary"                     = "— University",
    # Interactions: Vignette Income × Rs. Income (M1)
    "vincomeMiddle:factor(income_qui)2"      = "$910.000 × Quintile 2",
    "vincomeHigh:factor(income_qui)2"        = "$4.000.000 × Quintile 2",
    "vincomeMiddle:factor(income_qui)3"      = "$910.000 × Quintile 3",
    "vincomeHigh:factor(income_qui)3"        = "$4.000.000 × Quintile 3",
    "vincomeMiddle:factor(income_qui)4"      = "$910.000 × Quintile 4",
    "vincomeHigh:factor(income_qui)4"        = "$4.000.000 × Quintile 4",
    "vincomeMiddle:factor(income_qui)5"      = "$910.000 × Quintile 5",
    "vincomeHigh:factor(income_qui)5"        = "$4.000.000 × Quintile 5",
    # Interactions: Vignette Education × Rs. Education (M2)
    "veduMiddle:educatSecondary"             = "High school × Secondary",
    "veduHigh:educatSecondary"               = "Universitary × Secondary",
    "veduMiddle:educatTechnical"             = "High school × Technical",
    "veduHigh:educatTechnical"               = "Universitary × Technical",
    "veduMiddle:educatUniversitary"          = "High school × University",
    "veduHigh:educatUniversitary"            = "Universitary × University"
  ),
  groups = list(
    "Vig. Income (ref.=$500.000)"                           = 2:3,
    "Vig. Education (ref.=Primary)"                         = 4:5,
    "Rs: Income (ref.=Quintile 1)"                          = 6:9,
    "Rs: Education (ref.=Primary)"                          = 10:12,
    "Vig. Income × Rs. Income (ref.=Quintile 1)"            = 13:20,
    "Vig. Education × Rs. Education (ref.=Primary)"         = 21:26
  ),
  custom.gof.rows = list(
    "Resp. characteristics" = c("Yes", "Yes")
  )
)
```

```{r}
htmlreg(
  interactions[3:4],
  single.row = T,
  digits = 3,
  file = here::here("output/tables/tableS002b.html"),
  caption = "Table S2b: Multilevel regression models with cross-level interactions vignette migration and religion",
  caption.above = TRUE,
  custom.model.names = c(
    "M3: Migration",
    "M4: Religion"
  ),
  custom.coef.map = list(
    # Vignette Migration
    "vmigback2nd generation (Peruvian)"                       = "Peruvian",
    "vmigback1. Generation (Venezuelan)"                      = "Venezuelan",
    # Vignette Religion
    "noreligCatholic"                                         = "Catholic",
    "noreligEvangelical"                                      = "Evangelical",
    "noreligJewish"                                           = "Jewish",
    # Interactions: Vignette Migration × Rs. Migration (M3)
    "vmigback2nd generation (Peruvian):migrationVenezuela"    = "Peruvian × Venezuela",
    "vmigback1. Generation (Venezuelan):migrationVenezuela"   = "Venezuelan × Venezuela",
    "vmigback2nd generation (Peruvian):migrationPeru"         = "Peruvian × Peru",
    "vmigback1. Generation (Venezuelan):migrationPeru"        = "Venezuelan × Peru",
    "vmigback2nd generation (Peruvian):migrationBolivia"      = "Peruvian × Bolivia",
    "vmigback1. Generation (Venezuelan):migrationBolivia"     = "Venezuelan × Bolivia",
    "vmigback2nd generation (Peruvian):migrationOthers"       = "Peruvian × Others",
    "vmigback1. Generation (Venezuelan):migrationOthers"      = "Venezuelan × Others",
    # Interactions: Vignette Religion × Rs. Religion (M4)
    "noreligCatholic:religionsBeliever without affiliation"   = "Catholic × Believer w/o Affiliation",
    "noreligEvangelical:religionsBeliever without affiliation"= "Evangelical × Believer w/o Affiliation",
    "noreligJewish:religionsBeliever without affiliation"     = "Jewish × Believer w/o Affiliation",
    "noreligCatholic:religionsCatholic"                       = "Catholic × Catholic",
    "noreligEvangelical:religionsCatholic"                    = "Evangelical × Catholic",
    "noreligJewish:religionsCatholic"                         = "Jewish × Catholic",
    "noreligCatholic:religionsEvangelical"                    = "Catholic × Evangelical",
    "noreligEvangelical:religionsEvangelical"                 = "Evangelical × Evangelical",
    "noreligJewish:religionsEvangelical"                      = "Jewish × Evangelical",
    "noreligCatholic:religionsJewish"                         = "Catholic × Jewish",
    "noreligEvangelical:religionsJewish"                      = "Evangelical × Jewish",
    "noreligJewish:religionsJewish"                           = "Jewish × Jewish",
    "noreligCatholic:religionsPrefer not to answer"           = "Catholic × Prefer not to answer",
    "noreligEvangelical:religionsPrefer not to answer"        = "Evangelical × Prefer not to answer",
    "noreligJewish:religionsPrefer not to answer"             = "Jewish × Prefer not to answer",
    "(Intercept)"                                             = "Intercept"
  ),
  groups = list(
    "Vig. Migration (ref.=Chilean)"                           = 1:2,
    "Vig. Religion (ref.=No religious)"                       = 3:5,
    "Vig. Migration × Rs. Migration (ref.=Chilean)"           = 6:13,
    "Vig. Religion × Rs. Religion (ref.=Atheist/Agnostic)"   = 14:28
  ),
  custom.gof.rows = list(
    "Resp. characteristics" = c("Yes", "Yes")
  )  
)
```

```{r}
htmlreg(
  interactions[5:6],
  single.row = T,
  digits = 3,
  file = here::here("output/tables/tableS002c.html"),
  caption = "Table S2c: Multilevel regression models with cross-level interactions vignette human values and politics",
  caption.above = TRUE,
  custom.model.names = c(
    "M5: Human Values",
    "M6: Politics"
  ),
  custom.coef.map = list(
    # Vignette Human Values
    "selftransConservation"                                   = "Conservation",
    "selftransOpeness to change"                              = "Openness to Change",
    "selftransSelf-transcendence"                             = "Self-transcendence",
    # Vignette Politics
    "polcenterLeft-wing"                                      = "Left-wing",
    "polcenterRight-wing"                                     = "Right-wing",
    "polcenterUninterested"                                   = "Uninterested",
    # Interactions: Vignette Human Values × Rs. Human Values (M5)
    "selftransConservation:humanvalueopenness_change"         = "Conservation × Openness to Change",
    "selftransOpeness to change:humanvalueopenness_change"    = "Openness to Change × Openness to Change",
    "selftransSelf-transcendence:humanvalueopenness_change"   = "Self-transcendence × Openness to Change",
    "selftransConservation:humanvalueconservation"            = "Conservation × Conservation",
    "selftransOpeness to change:humanvalueconservation"       = "Openness to Change × Conservation",
    "selftransSelf-transcendence:humanvalueconservation"      = "Self-transcendence × Conservation",
    "selftransConservation:humanvalueself_transcendence"      = "Conservation × Self-transcendence",
    "selftransOpeness to change:humanvalueself_transcendence" = "Openness to Change × Self-transcendence",
    "selftransSelf-transcendence:humanvalueself_transcendence"= "Self-transcendence × Self-transcendence",
    # Interactions: Vignette Politics × Rs. Ideology (M6)
    "polcenterLeft-wing:ideology_collapsedCenter"             = "Left-wing × Center",
    "polcenterRight-wing:ideology_collapsedCenter"            = "Right-wing × Center",
    "polcenterUninterested:ideology_collapsedCenter"          = "Uninterested × Center",
    "polcenterLeft-wing:ideology_collapsedRight"              = "Left-wing × Right",
    "polcenterRight-wing:ideology_collapsedRight"             = "Right-wing × Right",
    "polcenterUninterested:ideology_collapsedRight"           = "Uninterested × Right",
    "polcenterLeft-wing:ideology_collapsedNon-Partisan"       = "Left-wing × Non-Partisan",
    "polcenterRight-wing:ideology_collapsedNon-Partisan"      = "Right-wing × Non-Partisan",
    "polcenterUninterested:ideology_collapsedNon-Partisan"    = "Uninterested × Non-Partisan",
    "(Intercept)"                                             = "Intercept"
  ),
  groups = list(
    "Vig. Human Values (ref.=Self-enhancement)"               = 1:3,
    "Vig. Politics (ref.=Center)"                             = 4:6,
    "Vig. Human Values × Rs. Human Values (ref.=Self-enhancement)" = 7:15,
    "Vig. Politics × Rs. Ideology (ref.=Left)"                = 16:24
  ),
  custom.gof.rows = list(
    "Resp. characteristics" = c("Yes", "Yes")
  )
)

library(marginaleffects)
plot_slopes(
  interactions[[3]],
  variables = "vmigback",
  by        = "migration"
) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(
    title = "Effect of Vignette Migration Background\nby Respondent Migration Background",
    x     = "Respondent Migration Background",
    y     = "Average Marginal Effect"
  ) +
  theme_minimal()
```

```{r AMEs-trust}
library(marginaleffects)
library(ggplot2)
library(dplyr)

# ── M1: Vignette Income × Respondent Income ──────────────────────────────────

ame_income <- avg_slopes(
  interactions[[1]],
  variables = "vincome",
  by        = "income_qui"
)

ame_income_plot <- ame_income |>
  mutate(
    contrast = case_when(
      contrast == "mean(Middle) - mean(Low)" ~ "Middle vignette\nvs. Low",
      contrast == "mean(High) - mean(Low)"   ~ "High vignette\nvs. Low"
    ),
    income_qui = factor(income_qui, levels = c(1, 2, 3, 4, 5),
                        labels = c("Quintile 1", "Quintile 2", "Quintile 3",
                                   "Quintile 4", "Quintile 5"))
  )

ggplot(ame_income_plot,
       aes(x = estimate, y = income_qui,
           xmin = conf.low, xmax = conf.high,
           color = estimate > 0)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_text(aes(label = sprintf("%.3f", estimate)),
            hjust = 0.5, vjust = -0.8, size = 3, show.legend = FALSE) +
  facet_wrap(~ contrast, ncol = 2) +
  scale_color_manual(
    values = c("TRUE" = "#2166ac", "FALSE" = "#d6604d"),
    labels = c("TRUE" = "Positive", "FALSE" = "Negative"),
    name   = "Direction"
  ) +
  labs(
    title    = "Average Marginal Effect of Vignette Income\nby Respondent Income Quintile",
    subtitle = "Reference category: Low income vignette",
    x        = "Average Marginal Effect (SD)",
    y        = "Respondent Income Quintile",
    caption  = "Note: Points represent average marginal effects (AME) in standard deviation units.\nError bars denote 95% confidence intervals. AMEs are computed averaging over all other\ncovariates in the model. Reference category for vignette income is Low ($500.000)."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "bottom",
    strip.text       = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    plot.caption     = element_text(hjust = 0, size = 8, color = "grey40")
  )

ggsave(
  plot     = last_plot(),
  filename = "fig_ame_income_CL.png",
  device   = "png",
  path     = "output/images/",
  width    = 2.5, height = 2., units = "cm", scale = 10
)

# ── M2: Vignette Education × Respondent Education ────────────────────────────

ame_education <- avg_slopes(
  interactions[[2]],
  variables = "vedu",
  by        = "educat"
)

ame_education_plot <- ame_education |>
  mutate(
    contrast = case_when(
      contrast == "mean(Middle) - mean(Low)" ~ "High school vignette\nvs. Primary",
      contrast == "mean(High) - mean(Low)"   ~ "University vignette\nvs. Primary"
    ),
    educat = factor(educat, levels = c("Primary", "Secondary", "Technical", "Universitary"))
  )

ggplot(ame_education_plot,
       aes(x = estimate, y = educat,
           xmin = conf.low, xmax = conf.high,
           color = estimate > 0)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_text(aes(label = sprintf("%.3f", estimate)),
            hjust = 0.5, vjust = -0.8, size = 3, show.legend = FALSE) +
  facet_wrap(~ contrast, ncol = 2) +
  scale_color_manual(
    values = c("TRUE" = "#2166ac", "FALSE" = "#d6604d"),
    labels = c("TRUE" = "Positive", "FALSE" = "Negative"),
    name   = "Direction"
  ) +
  labs(
    title    = "Average Marginal Effect of Vignette Education\nby Respondent Education",
    subtitle = "Reference category: Primary education vignette",
    x        = "Average Marginal Effect (SD)",
    y        = "Respondent Education",
    caption  = "Note: Points represent average marginal effects (AME) in standard deviation units.\nError bars denote 95% confidence intervals. AMEs are computed averaging over all other\ncovariates in the model. Reference category for vignette education is Primary."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "bottom",
    strip.text       = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    plot.caption     = element_text(hjust = 0, size = 8, color = "grey40")
  )

ggsave(
  plot     = last_plot(),
  filename = "fig_ame_education_CL.png",
  device   = "png",
  path     = "output/images/",
  width    = 2.5, height = 2., units = "cm", scale = 10
)

# ── M3: Vignette Migration × Respondent Migration ────────────────────────────

ame_migration <- avg_slopes(
  interactions[[3]],
  variables = "vmigback",
  by        = "migration"
)

ame_migration_plot <- ame_migration |>
  mutate(
    contrast = case_when(
      contrast == "mean(2nd generation (Peruvian)) - mean(No migration background)" ~ "Peruvian vignette\nvs. Chilean",
      contrast == "mean(1. Generation (Venezuelan)) - mean(No migration background)" ~ "Venezuelan vignette\nvs. Chilean"
    ),
    migration = factor(migration, levels = c("Chile", "Venezuela", "Peru", "Bolivia", "Others"))
  )

ggplot(ame_migration_plot,
       aes(x = estimate, y = migration,
           xmin = conf.low, xmax = conf.high,
           color = estimate > 0)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_text(aes(label = sprintf("%.3f", estimate)),
            hjust = 0.5, vjust = -0.8, size = 3, show.legend = FALSE) +
  facet_wrap(~ contrast, ncol = 2) +
  scale_color_manual(
    values = c("TRUE" = "#2166ac", "FALSE" = "#d6604d"),
    labels = c("TRUE" = "Positive", "FALSE" = "Negative"),
    name   = "Direction"
  ) +
  labs(
    title    = "Average Marginal Effect of Vignette Migration\nby Respondent Migration Background",
    subtitle = "Reference category: Chilean vignette",
    x        = "Average Marginal Effect (SD)",
    y        = "Respondent Migration Background",
    caption  = "Note: Points represent average marginal effects (AME) in standard deviation units.\nError bars denote 95% confidence intervals. AMEs are computed averaging over all other\ncovariates in the model. Reference category for vignette migration is Chilean."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "bottom",
    strip.text       = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    plot.caption     = element_text(hjust = 0, size = 8, color = "grey40")
  )

ggsave(
  plot     = last_plot(),
  filename = "fig_ame_migration_CL.png",
  device   = "png",
  path     = "output/images/",
  width    = 2.5, height = 2., units = "cm", scale = 10
)

# ── M4: Vignette Religion × Respondent Religion ──────────────────────────────

ame_religion <- avg_slopes(
  interactions[[4]],
  variables = "norelig",
  by        = "religions"
)

ame_religion_plot <- ame_religion |>
  mutate(
    contrast = case_when(
      contrast == "mean(Catholic) - mean(Non-religious)"    ~ "Catholic vignette\nvs. Non-religious",
      contrast == "mean(Evangelical) - mean(Non-religious)" ~ "Evangelical vignette\nvs. Non-religious",
      contrast == "mean(Jewish) - mean(Non-religious)"      ~ "Jewish vignette\nvs. Non-religious"
    ),
    religions = factor(religions, levels = c(
      "Non-religious",
      "Believer without affiliation",
      "Catholic",
      "Evangelical",
      "Jewish",
      "Prefer not to answer"
    ))
  )

ggplot(ame_religion_plot,
       aes(x = estimate, y = religions,
           xmin = conf.low, xmax = conf.high,
           color = estimate > 0)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_text(aes(label = sprintf("%.3f", estimate)),
            hjust = 0.5, vjust = -0.8, size = 3, show.legend = FALSE) +
  facet_wrap(~ contrast, ncol = 3) +
  scale_color_manual(
    values = c("TRUE" = "#2166ac", "FALSE" = "#d6604d"),
    labels = c("TRUE" = "Positive", "FALSE" = "Negative"),
    name   = "Direction"
  ) +
  labs(
    title    = "Average Marginal Effect of Vignette Religion\nby Respondent Religion",
    subtitle = "Reference category: Non-religious vignette",
    x        = "Average Marginal Effect (SD)",
    y        = "Respondent Religion",
    caption  = "Note: Points represent average marginal effects (AME) in standard deviation units.\nError bars denote 95% confidence intervals. AMEs are computed averaging over all other\ncovariates in the model. Reference category for vignette religion is Non-religious."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "bottom",
    strip.text       = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    plot.caption     = element_text(hjust = 0, size = 8, color = "grey40")
  )

ggsave(
  plot     = last_plot(),
  filename = "fig_ame_religion_CL.png",
  device   = "png",
  path     = "output/images/",
  width    = 2.5, height = 2., units = "cm", scale = 10
)

# ── M5: Vignette Human Values × Respondent Human Values ──────────────────────

ame_humanvalues <- avg_slopes(
  interactions[[5]],
  variables = "selftrans",
  by        = "humanvalue"
)

ame_humanvalues_plot <- ame_humanvalues |>
  mutate(
    contrast = case_when(
      contrast == "mean(Conservation) - mean(Self-enhancement)"     ~ "Conservation vignette\nvs. Self-enhancement",
      contrast == "mean(Openess to change) - mean(Self-enhancement)"~ "Openness to Change vignette\nvs. Self-enhancement",
      contrast == "mean(Self-transcendence) - mean(Self-enhancement)"~ "Self-transcendence vignette\nvs. Self-enhancement"
    ),
    humanvalue = factor(humanvalue, levels = c(
      "self_enhancement",
      "conservation",
      "openness_change",
      "self_transcendence"
    ),
    labels = c(
      "Self-enhancement",
      "Conservation",
      "Openness to Change",
      "Self-transcendence"
    ))
  )

ggplot(ame_humanvalues_plot,
       aes(x = estimate, y = humanvalue,
           xmin = conf.low, xmax = conf.high,
           color = estimate > 0)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_text(aes(label = sprintf("%.3f", estimate)),
            hjust = 0.5, vjust = -0.8, size = 3, show.legend = FALSE) +
  facet_wrap(~ contrast, ncol = 3) +
  scale_color_manual(
    values = c("TRUE" = "#2166ac", "FALSE" = "#d6604d"),
    labels = c("TRUE" = "Positive", "FALSE" = "Negative"),
    name   = "Direction"
  ) +
  labs(
    title    = "Average Marginal Effect of Vignette Human Values\nby Respondent Human Values",
    subtitle = "Reference category: Self-enhancement vignette",
    x        = "Average Marginal Effect (SD)",
    y        = "Respondent Human Values",
    caption  = "Note: Points represent average marginal effects (AME) in standard deviation units.\nError bars denote 95% confidence intervals. AMEs are computed averaging over all other\ncovariates in the model. Reference category for vignette human values is Self-enhancement."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "bottom",
    strip.text       = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    plot.caption     = element_text(hjust = 0, size = 8, color = "grey40")
  )

ggsave(
  plot     = last_plot(),
  filename = "fig_ame_humanvalues_CL.png",
  device   = "png",
  path     = "output/images/",
  width    = 2.5, height = 2., units = "cm", scale = 10
)

# ── M6: Vignette Politics × Respondent Ideology ──────────────────────────────

ame_politics <- avg_slopes(
  interactions[[6]],
  variables = "polcenter",
  by        = "ideology_collapsed"
)

ame_politics_plot <- ame_politics |>
  mutate(
    contrast = case_when(
      contrast == "mean(Left-wing) - mean(Center)"     ~ "Left-wing vignette\nvs. Center",
      contrast == "mean(Right-wing) - mean(Center)"    ~ "Right-wing vignette\nvs. Center",
      contrast == "mean(Uninterested) - mean(Center)"  ~ "Uninterested vignette\nvs. Center"
    ),
    ideology_collapsed = factor(ideology_collapsed,
                                levels = c("Left", "Center", "Right", "Non-Partisan"))
  )

ggplot(ame_politics_plot,
       aes(x = estimate, y = ideology_collapsed,
           xmin = conf.low, xmax = conf.high,
           color = estimate > 0)) +
  geom_pointrange() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_text(aes(label = sprintf("%.3f", estimate)),
            hjust = 0.5, vjust = -0.8, size = 3, show.legend = FALSE) +
  facet_wrap(~ contrast, ncol = 3) +
  scale_color_manual(
    values = c("TRUE" = "#2166ac", "FALSE" = "#d6604d"),
    labels = c("TRUE" = "Positive", "FALSE" = "Negative"),
    name   = "Direction"
  ) +
  labs(
    title    = "Average Marginal Effect of Vignette Politics\nby Respondent Ideology",
    subtitle = "Reference category: Center vignette",
    x        = "Average Marginal Effect (SD)",
    y        = "Respondent Ideology",
    caption  = "Note: Points represent average marginal effects (AME) in standard deviation units.\nError bars denote 95% confidence intervals. AMEs are computed averaging over all other\ncovariates in the model. Reference category for vignette politics is Center."
  ) +
  theme_minimal() +
  theme(
    legend.position  = "bottom",
    strip.text       = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    plot.caption     = element_text(hjust = 0, size = 8, color = "grey40")
  )

ggsave(
  plot     = last_plot(),
  filename = "fig_ame_politics_CL.png",
  device   = "png",
  path     = "output/images/",
  width    = 2.5, height = 2., units = "cm", scale = 10
)
```



```{r coefplot-trust}
# Extract coefficients and confidence intervals using broom
library(broom.mixed)
coef_data <- broom.mixed::tidy(lm_fship_vig_resp, conf.int = TRUE)
coef_data <- coef_data %>% filter(term %in% c(
  "vincomeMiddle", "vincomeHigh", "veduMiddle", "veduHigh", 
  "noreligCatholic", "noreligEvangelical", "noreligJewish", 
  "vmigback2nd generation (Peruvian)", "vmigback1. Generation (Venezuelan)", 
  "polcenterLeft-wing", "polcenterRight-wing", "polcenterUninterested", 
  "selftransConservation", "selftransOpeness to change", "selftransSelf-transcendence"))

coef_data <-coef_data %>%  add_row(term = "**Income (ref: $500K)**",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 1)
coef_data <-coef_data %>%  add_row(term = "**Education (ref: Primary)**",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 4) 
coef_data <-coef_data %>%  add_row(term = "**Religion (ref: Non-religious)**",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 7)
coef_data <-coef_data %>%  add_row(term = "**Migration (ref: No-mig. back.)**",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 11)
coef_data <-coef_data %>%  add_row(term = "**Political pos. (ref: Center)**",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 14)
coef_data <-coef_data %>%  add_row(term = "**Values (ref: Self-enhancement)**",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 18)

coef_data$term <- factor(coef_data$term,
                         levels = rev(
                           c("**Income (ref: $500K)**","vincomeMiddle", "vincomeHigh",
                             "**Education (ref: Primary)**","veduMiddle", "veduHigh",
                             "**Religion (ref: Non-religious)**","noreligCatholic", "noreligEvangelical", "noreligJewish",
                             "**Migration (ref: No-mig. back.)**","vmigback2nd generation (Peruvian)", "vmigback1. Generation (Venezuelan)",
                             "**Political pos. (ref: Center)**","polcenterLeft-wing", "polcenterRight-wing", "polcenterUninterested",
                             "**Values (ref: Self-enhancement)**","selftransConservation", "selftransOpeness to change", "selftransSelf-transcendence")),
  labels = 
    rev(c("**Income (ref: $500K)**","$910K", "$4100K", 
          "**Education (ref: Primary)**","Secondary Education", "University Education",
          "**Religion (ref: Non-religious)**","Catholic", "Evangelical", "Jewish",
          "**Migration (ref: No-mig. back.)**","2nd generation (Peruvian)", "1st. Generation (Venezuelan)",
          "**Political pos. (ref: Center)**","Left-wing", "Right-wing", "Uninterested",
          "**Values (ref: Self-enhancement)**","Conservation", "Openness to change", "Self-transcendence")))


coef_data$coef_lab<- paste0(round(coef_data$estimate,3)," (",round(coef_data$std.error,2),")")
coef_data$coef_lab <- car::recode(coef_data$coef_lab,recodes = "'NA (NA)'=' '")


library(ggthemes)
library(ggtext) #markdown
library(ggplot2)
# Create the coefficient plot
ggplot(coef_data, aes(x = estimate, y = term,label=coef_lab)) +
  geom_vline(xintercept = 0,
             color = "red",
             size = 1) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0.2,
    color = "darkgray",
    size = 1
  ) +  # Confidence intervals
  geom_point(size = 3, color = "black") +  # Points for coefficient estimates
  geom_text(vjust = 0, nudge_y = 0.3) +  
  labs(
    title = "[Get along]: Imagine you know person [ID] through your circle of acquaintances.\nHow likely is it that you would get along with person [ID]?",
    subtitle = "Not likely at all ←                       → Absolutely likely",
    x = "Standardized coefficient",
    y = NULL
  ) +
  # scale_x_continuous(limits = c(-0.65,0.9)) +
  theme(
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 13),
    legend.title = element_text(face = "bold"),
    strip.text = element_text(face = "bold"),
    axis.title = element_text(face = "bold"),
    axis.title.x = element_text(margin = margin(t = 10), hjust = 0),
    axis.title.y = element_text(margin = margin(r = 10), hjust = 1),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none",
    axis.text.y = element_markdown(hjust = 1, size = 16),
    plot.caption = element_markdown(hjust = 1, size = 13)
  )  
  
ggsave(plot = last_plot(),filename = "fig_coefplot_friendship_CL.png",device = "png",path = "output/images/",width = 2.5,height = 2.,units = "cm",scale = 10)
```

```{r}
# Conditional predictions (including random effects)

predicted_friendship <- 
marginaleffects::predictions(lm_fship_vig_resp) %>% 
  broom::tidy() %>% 
  select(friendship_pred=estimate,conf.low,conf.high)

df_vig$friendship_pred <- predicted_friendship$friendship_pred
df_vig$friendship_pred_lw <- predicted_friendship$conf.low
df_vig$friendship_pred_hi <- predicted_friendship$conf.high

df_vig$friendship_pred_ptile <- ntile(df_vig$friendship_pred,100)

df_rank_vignettes <- df_vig %>% 
  filter(friendship_pred_ptile %in% c(1,25,50,75,99)) %>% 
  arrange(friendship,friendship_pred_ptile,friendship_pred,friendship_pred_ptile)
set.seed(123)
df_rank_vignettes_subsample <- 
df_rank_vignettes %>% select(friendship_pred,friendship_pred_lw,
                             friendship_pred_hi,friendship_pred_ptile,
                             vincome:vage) %>%  
  group_by(friendship_pred_ptile) %>%
  slice_sample(n = 1) %>%
  ungroup() 

library(ggplot2)
#########################################-
## Assuming df_rank_vignettes contains ##-
#########################################-
# - friendship_pred (point estimate)
# - friendship_pred_lw (lower bound)
# - friendship_pred_hi (upper bound)
# - friendship_pred_ptile (percentile group: 1, 25, 50, 75, 99)

# Treat percentile as numeric (better spacing) ---------------------------------|
ggplot(df_rank_vignettes_subsample, aes(x = friendship_pred_ptile, y = friendship_pred)) +
  geom_point(size = 3, color = "darkblue") +
  geom_errorbar(aes(ymin = friendship_pred_lw, ymax = friendship_pred_hi), 
                width = 5, linewidth = 0.8, color = "darkblue") +
  scale_x_continuous(breaks = c(1, 25, 50, 75, 99),  
                     sec.axis = sec_axis(~ ., 
                      breaks = c(1, 25, 50, 75, 99), 
                      labels = paste(df_rank_vignettes_subsample$vincome,df_rank_vignettes_subsample$vedu,
      df_rank_vignettes_subsample$vmigback,df_rank_vignettes_subsample$norelig,
      df_rank_vignettes_subsample$polcenter,df_rank_vignettes_subsample$selftrans))
                     ) +
  labs(x = "Percentile group", 
       y = "Friendship prediction (95% CI)") +
  theme_minimal(base_size = 12) +
  coord_flip()+
  theme(panel.grid.minor = element_blank())
```

```{r mfcurve-trust}
predicted_friendship <- 
marginaleffects::predictions(lm_fship_vig_resp) %>% 
  broom::tidy() %>% 
  select(friendship_pred=estimate,conf.low,conf.high)

df_vig$friendship_pred <- predicted_friendship$friendship_pred
df_vig$friendship_pred_lw <- predicted_friendship$conf.low
df_vig$friendship_pred_hi <- predicted_friendship$conf.high

df_vig$friendship_pred_ptile <- ntile(df_vig$friendship_pred,100)

df_vig$vmigback

library(mfcurve)
library(plotly)
# Create mfcurve plot
mfcurve(
  data = df_vig,
  outcome = "friendship_pred",
  factors = c("vincome","vedu","norelig","vmigback","polcenter","selftrans"),
  test = "mean",mode = "expanded",showGrandMean = F,showSigStars = F,showTitle = F
  )

mfcurve_plotting(
  data = df_vig,
  outcome = "friendship_pred",
  factors = c("vincome","vedu","norelig","vmigback","polcenter","selftrans"),
  test = "mean",mode = "expanded",showGrandMean = F,showSigStars = F,showTitle = F,SaveProcessedData = T
  )


mfcurve_df <- 
mfcurve_preprocessing(  data = df_vig,
  outcome = "friendship_pred",
  factors = c("vincome","vedu","norelig","vmigback","polcenter","selftrans"),
  test = "mean")


mfcurve_df$lower_data$labels <- factor(
  mfcurve_df$lower_data$factor,
  levels = c("vincome", "vedu", "norelig", "vmigback", "polcenter", "selftrans"),
  labels = c("Income", "Education", "Religion", "Migration", "Political", "Values")
)


mfcurve_df$lower_data$factor <- mfcurve_df$lower_data$labels 

mfcurve_df$lower_data$rank

mfcurve_plotting(group_stats_vis = mfcurve_df$group_stats_vis,lower_data = mfcurve_df$lower_data,
  outcome = "friendship_pred",grand_mean = mfcurve_df$grand_mean,factors = mfcurve_df$lower_data$factor,level = mfcurve_df$level,
  mode = "expanded",
  showGrandMean = F,showSigStars = F,showTitle = F
  )

```

```{r Predicted-trust}
library(marginaleffects) 
library(ggplot2)
library(dplyr)
library(lme4)

df_plot_income <- predictions(cl_trust_inco,by = c("vincome", "income_qui"))
df_plot_educ   <- predictions(cl_trust_educ, by = c("vedu", "educat"))
df_plot_mig    <- predictions(cl_trust_migr, by = c("vmigback", "migration"))
df_plot_reli   <- predictions(cl_trust_reli, by = c("norelig", "religions"))
df_plot_valu   <- predictions(cl_trust_vals, by = c("selftrans", "humanvalue"))
df_plot_poli   <- predictions(cl_trust_poli, by = c("polcenter", "ideology_collapsed"))

df_plot_income$income_qui <- as.factor(as.numeric(df_plot_income$income_qui))

plot_income <- 
df_plot_income %>%
  filter(income_qui %in% c("1","3","5")) %>%
ggplot(aes(y =estimate,x=vincome, group=income_qui,color=income_qui,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid") +
  geom_line(size=1) +
  geom_point(size=2) +
  scale_color_manual(labels = c("Bottom (Q1)","Middle (Q3)","Top (Q5)"),values=c("#323232","pink","#989898"))+
  scale_y_continuous(limits = c(-1,1))+
  labs(
    # caption = paste0("Note: N (observations) = ",nobs(cl_trust_inco),"; N (individuals) = ",lme4::ngrps(cl_trust_inco),". Predictive estimates with 95% confidence intervals"),
       x="Income (Vignette)",y="Get along",
       color="Income (R's)",
       fill="Income (R's)") +
  theme(legend.position = "bottom");plot_income

# ggsave(plot = last_plot(),filename = "figure001_CL.png",device = "png",
#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)

plot_education <- 
df_plot_educ %>%
  filter(educat %in% c("Universitary","Primary")) %>% 
ggplot(aes(y =estimate,x=vedu, fill=educat, group=educat,color=educat,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid") +
  geom_line(size=1) +
  geom_point(size=2) +
  scale_color_manual(values=c("#323232","#989898","#CCCCCC","red"))+
  scale_y_continuous(limits = c(-1,1))+
  labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_educ),"; N (individuals) = ",lme4::ngrps(cl_trust_educ),". Predictive estimates with 95% confidence intervals"),
       x="Education (Vignette)",y="Get along",
       color="Education (R's)",
       fill="Education (R's)") +
  theme(legend.position = "bottom");plot_education

# ggsave(plot = last_plot(),filename = "figure002_CL.png",device = "png",
#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)

plot_migration <- 
df_plot_mig %>% 
  filter(migration %in% c("Chile","Venezuela","Peru")) %>%
  ggplot(aes(y =estimate,x=vmigback, fill=migration, group=migration,color=migration,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  # scale_color_manual(values=c("red","purple","#027A24"))+
  scale_y_continuous(limits = c(-1,1)) +
      labs(
        # caption = paste0("Note: N (observations) = ",nobs(cl_trust_migr),"; N (individuals) = ",lme4::ngrps(cl_trust_migr),
                            # ". Predictive estimates with 95% confidence intervals.\nOther migration groups included, not depicted."),
       x="Migration (Vignette)",y="Get along",
       color="Migration (R's)",
       fill="Migration (R's)") +
  theme(legend.position = "bottom");plot_migration

# ggsave(plot = last_plot(),filename = "figure003_CL.png",device = "png",
#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)

plot_relig <- 
df_plot_reli %>% 
  filter(!religions %in% c("Jewish","Prefer not to answer")) %>%
  ggplot(aes(y =estimate,x=norelig, fill=religions, group=religions,color=religions,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  scale_color_manual(values=c("black","darkgray","lightblue","darkblue","blue","orange"))+
  # scale_color_viridis_d()+
    # scale_color_stata()+
  scale_y_continuous(limits = c(-1,1)) +
      labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_reli),"; N (individuals) = ",lme4::ngrps(cl_trust_reli),
                            ". Predictive estimates with 95% confidence intervals."),
       x="Religion (Vignette)",y="Get along",
       color="Religion (R's)",
       fill="Religion\ (R's)") +
     theme(
    legend.position = "bottom",
    # legend.background = element_rect(fill = "white", color = "gray70", linewidth = 0.3),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9),
    # axis.text.x = element_text(angle = 20, hjust = 1),
    plot.title = element_text(face = "bold")
  );plot_relig

# ggsave(plot = last_plot(),filename = "figure004_CL.png",device = "png",
#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)

df_plot_poli$polcenter <- factor(df_plot_poli$polcenter,levels = c("Uninterested","Left-wing", "Center", "Right-wing"))
plot_political <- 
df_plot_poli %>%
ggplot(aes(y =estimate,x=polcenter, fill=ideology_collapsed, group=ideology_collapsed,color=ideology_collapsed,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.1,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  scale_color_manual(values=c("red","purple","blue","darkgray"))+
  scale_y_continuous(limits = c(-1,1)) +
  labs(
    # caption = paste0("Note: N (observations) = ",nobs(cl_trust_poli),"; N (individuals) = ",lme4::ngrps(cl_trust_poli),". Predictive estimates with 95% confidence intervals"),
       x="Political (Vignette)",y="Get along",
       color="Political (R's)",
       fill="Political (R's)") +
  theme(legend.position = "bottom");plot_political

# ggsave(plot = last_plot(),filename = "figure005_CL.png",device = "png",
#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)

plot_values <- 
df_plot_valu %>% 
  ggplot(aes(y =estimate,x=selftrans, fill=humanvalue, group=humanvalue,color=humanvalue,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  # scale_color_manual(values=c("red","purple","#027A24"))+
  labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_vals),"; N (individuals) = ",lme4::ngrps(cl_trust_vals),". Predictive estimates with 95% confidence intervals"),
       x="Human Values (Vignette)",y="Get along",
       color="Human Values (R's)",
       fill="Human Values (R's)") +
  theme(legend.position = "bottom") + 
  scale_y_continuous(limits = c(-1,1)) +
     theme(
    # legend.position = c(0.93, 0.21),     # posición relativa (derecha-abajo)
    # legend.background = element_rect(fill = "white", color = "gray70", linewidth = 0.3),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 5),
    # axis.text.x = element_text(angle = 20, hjust = 1),
    plot.title = element_text(face = "bold")
  );plot_values
  
# ggsave(plot = last_plot(),filename = "figure006_CL.png",device = "png",
#        path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)


library(patchwork)

# Assuming your plots are named p1, p2, p3, p4
(plot_income | plot_education)  # 2x2 grid
ggsave(plot = last_plot(),filename = "figure_slides01_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 16)


(plot_migration | plot_relig)  # 2x2 grid
ggsave(plot = last_plot(),filename = "figure_slides02_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 16)

(plot_political | plot_values)  # 2x2 grid
ggsave(plot = last_plot(),filename = "figure_slides03_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 16)
```



```{r interactions-trust}
library(marginaleffects)
library(ggplot2)
library(dplyr)

options(future.globals.maxSize= 891289600)
df_plot_income <- plot_predictions(cl_trust_inco, condition = c("vincome", "income_qui"),draw = F)
df_plot_educ  <- plot_predictions(cl_trust_educ, condition = c("vedu", "educat"),draw = F)
df_plot_mig   <- plot_predictions(cl_trust_migr, condition = c("vmigback", "migration"),draw = F)
df_plot_reli  <- plot_predictions(cl_trust_reli, condition = c("norelig", "religions"),draw = F)
df_plot_valu  <- plot_predictions(cl_trust_vals, condition = c("selftrans", "humanvalue"),draw = F)
df_plot_poli  <- plot_predictions(cl_trust_poli, condition = c("polcenter", "ideology_collapsed"),draw = F)

df_plot_income$income_qui <- as.factor(as.numeric(df_plot_income$income_qui))

df_plot_income %>%
  filter(income_qui %in% c("1","5")) %>%
ggplot(aes(y =estimate,x=vincome, group=income_qui,color=income_qui,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid") +
  geom_line(size=1) +
  geom_point(size=2) +
  scale_color_manual(labels = c("Bottom 10%","Top 10%"),values=c("#323232","#989898"))+
  # scale_y_continuous(limits = c(5,10))+
  labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_inco),"; N (individuals) = ",lme4::ngrps(cl_trust_inco),". Predictive estimates with 95% confidence intervals"),
       x="Income (Vignette)",y="Trust (1-10)",
       color="Income\n(Respondent)",
       fill="Income\n(Respondent)") +
  theme(legend.position = "right")

ggsave(plot = last_plot(),filename = "figure001_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)


df_plot_educ %>%
  filter(educat %in% c("Universitary","Primary")) %>% 
ggplot(aes(y =estimate,x=vedu, fill=educat, group=educat,color=educat,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid") +
  geom_line(size=1) +
  geom_point(size=2) +
  scale_color_manual(values=c("#323232","#989898","#CCCCCC","red"))+
  scale_y_continuous(limits = c(5,10))+
  labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_educ),"; N (individuals) = ",lme4::ngrps(cl_trust_educ),". Predictive estimates with 95% confidence intervals"),
       x="Education (Vignette)",y="Trust (1-10)",
       color="Education\n(Respondent)",
       fill="Education\n(Respondent)") +
  theme(legend.position = "right")

ggsave(plot = last_plot(),filename = "figure002_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)


df_plot_mig %>% 
  filter(migration %in% c("Chile","Venezuela","Peru","Bolivia")) %>%
  ggplot(aes(y =estimate,x=vmigback, fill=migration, group=migration,color=migration,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  # scale_color_manual(values=c("red","purple","#027A24"))+
  scale_y_continuous(limits = c(5,10)) +
      labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_migr),"; N (individuals) = ",lme4::ngrps(cl_trust_migr),
                            ". Predictive estimates with 95% confidence intervals.\nOther migration groups included, not depicted."),
       x="Migration (Vignette)",y="Trust (1-10)",
       color="Migration\n(Respondent)",
       fill="Migration\n(Respondent)") +
  theme(legend.position = "right") 

ggsave(plot = last_plot(),filename = "figure003_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)


df_plot_reli %>% 
  ggplot(aes(y =estimate,x=norelig, fill=religions, group=religions,color=religions,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  scale_color_manual(values=c("black","darkgray","lightblue","darkblue","blue","orange"))+
  # scale_color_viridis_d()+
    # scale_color_stata()+
  scale_y_continuous(limits = c(5,10)) +
      labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_reli),"; N (individuals) = ",lme4::ngrps(cl_trust_reli),
                            ". Predictive estimates with 95% confidence intervals."),
       x="Religion (Vignette)",y="Trust (1-10)",
       color="Religion\n(Respondent)",
       fill="Religion\n(Respondent)") +
  theme(legend.position = "right") 

ggsave(plot = last_plot(),filename = "figure004_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)


df_plot_poli$polcenter <- factor(df_plot_poli$polcenter,levels = c("Uninterested","Left-wing", "Center", "Right-wing"))
df_plot_poli %>%
ggplot(aes(y =estimate,x=polcenter, fill=ideology_collapsed, group=ideology_collapsed,color=ideology_collapsed,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.1,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  scale_color_manual(values=c("red","purple","blue","darkgray"))+
  scale_y_continuous(limits = c(5,10))+
  labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_poli),"; N (individuals) = ",lme4::ngrps(cl_trust_poli),". Predictive estimates with 95% confidence intervals"),
       x="Political (Vignette)",y="Trust (1-10)",
       color="Political\n(Respondent)",
       fill="Political\n(Respondent)") +
  theme(legend.position = "right")

ggsave(plot = last_plot(),filename = "figure005_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)

df_plot_valu %>% 
  ggplot(aes(y =estimate,x=selftrans, fill=humanvalue, group=humanvalue,color=humanvalue,ymin=conf.low, ymax=conf.high)) +
  geom_errorbar(width=0.02,linetype="solid",position=position_dodge(width=0.4)) +
  # geom_line(size=1) +
  geom_point(size=2,position=position_dodge(width=0.4)) +
  # scale_color_manual(values=c("red","purple","#027A24"))+
  labs(caption = paste0("Note: N (observations) = ",nobs(cl_trust_vals),"; N (individuals) = ",lme4::ngrps(cl_trust_vals),". Predictive estimates with 95% confidence intervals"),
       x="Human Values (Vignette)",y="Trust (1-10)",
       color="Human Value: (Respondent)",
       fill="Human Value: (Respondent)") +
  theme(legend.position = "right") + 
  scale_y_continuous(limits = c(5,10)) + 
     theme(
    # legend.position = c(0.93, 0.21),     # posición relativa (derecha-abajo)
    legend.background = element_rect(fill = "white", color = "gray70", linewidth = 0.3),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9),
    # axis.text.x = element_text(angle = 20, hjust = 1),
    plot.title = element_text(face = "bold")
  )
  
ggsave(plot = last_plot(),filename = "figure006_CL.png",device = "png",
       path = here::here("output/images"),width = 2,height = 1,units = "cm",scale = 12)
```

# Models: Cooperation

2) Imagine you are faced with a task that you cannot perform on your own. How likely would you be to ask the person [ID] for help? 

```{r}
library(estimatr)
df_vig$cooperation_z <- scale(df_vig$cooperation);summary(df_vig$cooperation_z)
lm_vincome <- lm_robust(cooperation_z~factor(vincome),data = df_vig,clusters = pid)
lm_veduc <- lm_robust(cooperation_z~factor(vedu),data = df_vig,clusters = pid)
lm_socioeconomic <- lm_robust(cooperation_z~factor(vedu)+factor(vincome),data = df_vig,clusters = pid)

socioeconomic <- list(lm_vincome,lm_veduc,lm_socioeconomic)
screenreg(socioeconomic,include.ci=F)

lm_vreligion <- lm_robust(cooperation_z~norelig,data = df_vig,clusters = pid)
lm_vmigration <- lm_robust(cooperation_z~factor(vmigback),data = df_vig,clusters = pid)
lm_sociocultural <- lm_robust(cooperation_z~norelig+factor(vmigback),data = df_vig,clusters = pid)
sociocultural <- list(lm_vreligion,lm_vmigration,lm_sociocultural)

screenreg(sociocultural,include.ci=F)

lm_vpolcenter <- lm_robust(cooperation_z~polcenter,data = df_vig,clusters = pid)
lm_vhumvalues <- lm_robust(cooperation_z~selftrans,data = df_vig,clusters = pid)
lm_political_values <- lm_robust(cooperation_z~polcenter+selftrans,data = df_vig,clusters = pid)
political_values <- list(lm_vpolcenter,lm_vhumvalues,lm_political_values)

screenreg(political_values,include.ci=F)

library(plm)
lm_SES <- plm(cooperation_z~vincome+vedu,data = df_vig,index = "pid")
lm_SES_rel <- plm(cooperation_z~vincome+vedu+norelig,data = df_vig,index = "pid")
lm_SES_rel_mig <- plm(cooperation_z~vincome+vedu+norelig+vmigback,data = df_vig,index = "pid")
lm_SES_rel_mig_pol <- plm(cooperation_z~vincome+vedu+norelig+vmigback+polcenter,data = df_vig,index = "pid")
lm_SES_rel_mig_pol_values <- plm(cooperation_z~vincome+vedu+norelig+vmigback+polcenter+selftrans,data = df_vig,index = "pid")
lm_SES_rel_mig_pol_values_controls <- plm(cooperation_z~vincome+vedu+norelig+vmigback+polcenter+selftrans+vgender+vage+vempstat,data = df_vig,index = "pid")

models_cooperation<- list(lm_SES,lm_SES_rel,lm_SES_rel_mig,lm_SES_rel_mig_pol,lm_SES_rel_mig_pol_values,lm_SES_rel_mig_pol_values_controls)
screenreg(models_cooperation,include.ci=F)

# Extract coefficients and confidence intervals using broom
coef_data <- broom::tidy(models_cooperation[[6]], conf.int = TRUE)
coef_data <- coef_data %>% filter(term %in% c(
  "vincomeMiddle", "vincomeHigh", "veduMiddle", "veduHigh", 
  "noreligCatholic", "noreligEvangelical", "noreligJewish", 
  "vmigback2nd generation (Peruvian)", "vmigback1. Generation (Venezuelan)", 
  "polcenterLeft-wing", "polcenterRight-wing", "polcenterUninterested", 
  "selftransConservation", "selftransOpeness to change", "selftransSelf-transcendence"))

coef_data <-coef_data %>%  add_row(term = "Income (ref: $500K)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 1)
coef_data <-coef_data %>%  add_row(term = "Education (ref: Primary)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 4) 
coef_data <-coef_data %>%  add_row(term = "Religion (ref: Non-religious)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 7)
coef_data <-coef_data %>%  add_row(term = "Migration (ref: No-mig. back.)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 11)
coef_data <-coef_data %>%  add_row(term = "Political pos. (ref: Center)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 14)
coef_data <-coef_data %>%  add_row(term = "Values (ref: Self-enhancement)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 18)

coef_data$term <- factor(coef_data$term,
                         levels = rev(
                           c("Income (ref: $500K)","vincomeMiddle", "vincomeHigh",
                             "Education (ref: Primary)","veduMiddle", "veduHigh",
                             "Religion (ref: Non-religious)","noreligCatholic", "noreligEvangelical", "noreligJewish",
                             "Migration (ref: No-mig. back.)","vmigback2nd generation (Peruvian)", "vmigback1. Generation (Venezuelan)",
                             "Political pos. (ref: Center)","polcenterLeft-wing", "polcenterRight-wing", "polcenterUninterested",
                             "Values (ref: Self-enhancement)","selftransConservation", "selftransOpeness to change", "selftransSelf-transcendence")),
  labels = 
    rev(c("Income (ref: $500K)","$910K", "$4100K", 
          "Education (ref: Primary)","Secondary Education", "University Education",
          "Religion (ref: Non-religious)","Catholic", "Evangelical", "Jewish",
          "Migration (ref: No-mig. back.)","2nd generation (Peruvian)", "1st. Generation (Venezuelan)",
          "Political pos. (ref: Center)","Left-wing", "Right-wing", "Uninterested",
          "Values (ref: Self-enhancement)","Conservation", "Openness to change", "Self-transcendence")))

library(ggthemes)
# Create the coefficient plot
ggplot(coef_data, aes(x = estimate, y = term)) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2, color = "darkgray",size=1) +  # Confidence intervals
  geom_point(size = 3, color = "black") +  # Points for coefficient estimates
  geom_vline(xintercept = 0,color="red",size=1) +
  labs(title = "[Cooperation]:Imagine you are faced with a task that you cannot perform on your own.\nHow likely would you be to ask the person [ID] for help?",
       subtitle = "Not likely at all ←                                                                          → Absolutely likely",
    x = "Standardized coefficient",
    y =NULL
  ) +
  # scale_x_continuous(limits = c(-0.65,0.65)) +
theme_minimal(base_family = "Roboto Condensed", base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        # Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1), color = "grey70"),
        # Italic, smaller, grey caption that is left-aligned
        plot.caption = element_text(face = "italic", size = rel(0.7), 
                                    color = "grey70", hjust = 0),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold, slightly larger facet titles that are left-aligned for the sake of repetition
        strip.text = element_text(face = "bold", size = rel(1.1), hjust = 0),
        # Bold axis titles
        axis.title = element_text(face = "bold"),
        # Add some space above the x-axis title and make it left-aligned
        axis.title.x = element_text(margin = margin(t = 10), hjust = 0),
        # Add some space to the right of the y-axis title and make it top-aligned
        axis.title.y = element_text(margin = margin(r = 10), hjust = 1))+
  theme(
    axis.text.y = element_text(hjust = 1,size = 13),
    plot.subtitle = element_text(hjust = 0.5)
  )

ggsave(plot = last_plot(),filename = "fig_coefplot_cooperation_CL.png",device = "png",path = "output/images/",width = 2.5,height = 2.,units = "cm",scale = 10)
```

# Models: Neighboorhood conflict

3)	Imagine that person [ID] moves into your neighborhood. How likely is it that you would come into conflict with that person?

```{r}
library(estimatr)
df_vig$neighborhood_z <- scale(df_vig$neighborhood);summary(df_vig$neighborhood)
lm_vincome <- lm_robust(neighborhood_z~factor(vincome),data = df_vig,clusters = pid)
lm_veduc <- lm_robust(neighborhood_z~factor(vedu),data = df_vig,clusters = pid)
lm_socioeconomic <- lm_robust(neighborhood_z~factor(vedu)+factor(vincome),data = df_vig,clusters = pid)

socioeconomic <- list(lm_vincome,lm_veduc,lm_socioeconomic)
screenreg(socioeconomic,include.ci=F)

lm_vreligion <- lm_robust(neighborhood_z~norelig,data = df_vig,clusters = pid)
lm_vmigration <- lm_robust(neighborhood_z~factor(vmigback),data = df_vig,clusters = pid)
lm_sociocultural <- lm_robust(neighborhood_z~norelig+factor(vmigback),data = df_vig,clusters = pid)
sociocultural <- list(lm_vreligion,lm_vmigration,lm_sociocultural)
screenreg(sociocultural,include.ci=F)

lm_vpolcenter <- lm_robust(neighborhood_z~polcenter,data = df_vig,clusters = pid)
lm_vhumvalues <- lm_robust(neighborhood_z~selftrans,data = df_vig,clusters = pid)
lm_political_values <- lm_robust(neighborhood_z~polcenter+selftrans,data = df_vig,clusters = pid)
political_values <- list(lm_vpolcenter,lm_vhumvalues,lm_political_values)

screenreg(political_values,include.ci=F)

library(plm)
lm_SES <- plm(neighborhood_z~vincome+vedu,data = df_vig,index = "pid")
lm_SES_rel <- plm(neighborhood_z~vincome+vedu+norelig,data = df_vig,index = "pid")
lm_SES_rel_mig <- plm(neighborhood_z~vincome+vedu+norelig+vmigback,data = df_vig,index = "pid")
lm_SES_rel_mig_pol <- plm(neighborhood_z~vincome+vedu+norelig+vmigback+polcenter,data = df_vig,index = "pid")
lm_SES_rel_mig_pol_values <- plm(neighborhood_z~vincome+vedu+norelig+vmigback+polcenter+selftrans,data = df_vig,index = "pid")
lm_SES_rel_mig_pol_values_controls <- plm(neighborhood_z~vincome+vedu+norelig+vmigback+polcenter+selftrans+vgender+vage+vempstat,data = df_vig,index = "pid")

models_neighborhood<- list(lm_SES,lm_SES_rel,lm_SES_rel_mig,lm_SES_rel_mig_pol,lm_SES_rel_mig_pol_values,lm_SES_rel_mig_pol_values_controls)
screenreg(models_neighborhood,include.ci=F)

# Extract coefficients and confidence intervals using broom
coef_data <- broom::tidy(models_neighborhood[[6]], conf.int = TRUE)
coef_data <- coef_data %>% filter(term %in% c(
  "vincomeMiddle", "vincomeHigh", "veduMiddle", "veduHigh", 
  "noreligCatholic", "noreligEvangelical", "noreligJewish", 
  "vmigback2nd generation (Peruvian)", "vmigback1. Generation (Venezuelan)", 
  "polcenterLeft-wing", "polcenterRight-wing", "polcenterUninterested", 
  "selftransConservation", "selftransOpeness to change", "selftransSelf-transcendence"))

coef_data <-coef_data %>%  add_row(term = "Income (ref: $500K)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 1)
coef_data <-coef_data %>%  add_row(term = "Education (ref: Primary)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 4) 
coef_data <-coef_data %>%  add_row(term = "Religion (ref: Non-religious)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 7)
coef_data <-coef_data %>%  add_row(term = "Migration (ref: No-mig. back.)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 11)
coef_data <-coef_data %>%  add_row(term = "Political pos. (ref: Center)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 14)
coef_data <-coef_data %>%  add_row(term = "Values (ref: Self-enhancement)",estimate = NA,conf.low = NA,conf.high = NA,std.error = NA,.before = 18)

coef_data$term <- factor(coef_data$term,
                         levels = rev(
                           c("Income (ref: $500K)","vincomeMiddle", "vincomeHigh",
                             "Education (ref: Primary)","veduMiddle", "veduHigh",
                             "Religion (ref: Non-religious)","noreligCatholic", "noreligEvangelical", "noreligJewish",
                             "Migration (ref: No-mig. back.)","vmigback2nd generation (Peruvian)", "vmigback1. Generation (Venezuelan)",
                             "Political pos. (ref: Center)","polcenterLeft-wing", "polcenterRight-wing", "polcenterUninterested",
                             "Values (ref: Self-enhancement)","selftransConservation", "selftransOpeness to change", "selftransSelf-transcendence")),
  labels = 
    rev(c("Income (ref: $500K)","$910K", "$4100K", 
          "Education (ref: Primary)","Secondary Education", "University Education",
          "Religion (ref: Non-religious)","Catholic", "Evangelical", "Jewish",
          "Migration (ref: No-mig. back.)","2nd generation (Peruvian)", "1st. Generation (Venezuelan)",
          "Political pos. (ref: Center)","Left-wing", "Right-wing", "Uninterested",
          "Values (ref: Self-enhancement)","Conservation", "Openness to change", "Self-transcendence")))

library(ggthemes)
# Create the coefficient plot
ggplot(coef_data, aes(x = estimate, y = term)) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2, color = "darkgray",size=1) +  # Confidence intervals
  geom_point(size = 3, color = "black") +  # Points for coefficient estimates
  geom_vline(xintercept = 0,color="red",size=1) +
  labs(title = "[Conflict]:Imagine that person [ID] moves into your neighborhood. \nHow likely is it that you would come into conflict with that person?",
       subtitle = "Not likely at all ←                                                                          → Absolutely likely",
    x = "Standardized coefficient",
    y =NULL
  ) +
  # scale_x_continuous(limits = c(-0.65,0.65)) +
theme_minimal(base_family = "Roboto Condensed", base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        # Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1), color = "grey70"),
        # Italic, smaller, grey caption that is left-aligned
        plot.caption = element_text(face = "italic", size = rel(0.7), 
                                    color = "grey70", hjust = 0),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold, slightly larger facet titles that are left-aligned for the sake of repetition
        strip.text = element_text(face = "bold", size = rel(1.1), hjust = 0),
        # Bold axis titles
        axis.title = element_text(face = "bold"),
        # Add some space above the x-axis title and make it left-aligned
        axis.title.x = element_text(margin = margin(t = 10), hjust = 0),
        # Add some space to the right of the y-axis title and make it top-aligned
        axis.title.y = element_text(margin = margin(r = 10), hjust = 1))+
  theme(
axis.text.y = element_markdown(hjust = 1, size = 16),
plot.caption = element_markdown(hjust = 1, size = 13)
  )

ggsave(plot = last_plot(),filename = "fig_coefplot_neighborhood_CL.png",device = "png",path = "output/images/",width = 2.5,height = 2,units = "cm",scale = 10)
```


```{r}
lm_vincome <- lm_robust(friendship_z~factor(vincome),data = df_vig,clusters = pid)
lm_veduc <- lm_robust(friendship_z~factor(vedu),data = df_vig,clusters = pid)
lm_socioeconomic <- lm_robust(friendship_z~factor(vedu)+factor(vincome),data = df_vig,clusters = pid)

socioeconomic <- list(lm_vincome,lm_veduc,lm_socioeconomic)

lm_vreligion <- lm_robust(friendship_z~norelig,data = df_vig,clusters = pid)
lm_vmigration <- lm_robust(friendship_z~factor(vmigback),data = df_vig,clusters = pid)
lm_sociocultural <- lm_robust(friendship_z~norelig+factor(vmigback),data = df_vig,clusters = pid)
sociocultural <- list(lm_vreligion,lm_vmigration,lm_sociocultural)

screenreg(sociocultural,include.ci=F)

lm_vpolcenter <- lm_robust(friendship_z~polcenter,data = df_vig,clusters = pid)
lm_vhumvalues <- lm_robust(friendship_z~selftrans,data = df_vig,clusters = pid)
lm_political_values <- lm_robust(friendship_z~polcenter+selftrans,data = df_vig,clusters = pid)
political_values <- list(lm_vpolcenter,lm_vhumvalues,lm_political_values)

screenreg(political_values,include.ci=F)

lm_SES <- plm(friendship_z~vincome+vedu,data = df_vig,index = "pid")
lm_SES_rel <- plm(friendship_z~vincome+vedu+norelig,data = df_vig,index = "pid")
lm_SES_rel_mig <- plm(friendship_z~vincome+vedu+norelig+vmigback,data = df_vig,index = "pid")
lm_SES_rel_mig_pol <- plm(friendship_z~vincome+vedu+norelig+vmigback+polcenter,data = df_vig,index = "pid")
lm_SES_rel_mig_pol_values <- plm(friendship_z~vincome+vedu+norelig+vmigback+polcenter+selftrans,data = df_vig,index = "pid")


lm_SES_rel_mig_pol_values_controls <- plm(friendship_z~vincome+vedu+norelig+vmigback+polcenter+selftrans+vgender+vage+vempstat,data = df_vig,index = "pid")

lm_SES_rel_mig_pol_values_controls_v2 <- plm(friendship_z~vincome+vedu+norelig+vmigback+polcenter+humanv+vgender+vage+vempstat,data = df_vig,index = "pid")


models_friendship<- list(lm_SES,lm_SES_rel,lm_SES_rel_mig,lm_SES_rel_mig_pol,lm_SES_rel_mig_pol_values,lm_SES_rel_mig_pol_values_controls)


screenreg(models_friendship,include.ci=F)

lm_friendship_mod <- lmer(friendship_z~vincome+vedu+educat+norelig+vmigback+polcenter+selftrans+vgender+vage+vempstat +(1|pid),data = df_vig)

lm_friendship_mod_v2 <- lmer(friendship_z~vincome+vedu+educat+norelig+vmigback+polcenter+selftrans+vgender+vage+vempstat +(1|pid),data = df_vig)




lm_friendship_mod1   <- lmer(friendship_z~vincome+vedu*educat+norelig+vmigback+polcenter+selftrans+vgender+vage+vempstat +(vedu|pid),data = df_vig)
lm_friendship_mod1.1 <- lmer(friendship_z~vincome*factor(income_qui)+vedu+educat+norelig+vmigback+polcenter+selftrans+vgender+vage+vempstat +(vincome|pid),data = df_vig)
lm_friendship_mod2   <- lmer(friendship_z~vincome+vedu+norelig+vmigback+polcenter*ideology_collapsed+selftrans+vgender+vage+vempstat +(polcenter|pid),data = df_vig)

lm_friendship_mod31   <- lmer(friendship_z~vincome+vedu+norelig+vmigback+migration+polcenter+ideology_collapsed+selftrans+vgender+vage+vempstat +(1|pid),data = df_vig)
lm_friendship_mod3   <- lmer(friendship_z~vincome+vedu+norelig+vmigback*migration+polcenter+ideology_collapsed+selftrans+vgender+vage+vempstat +(migration|pid),data = df_vig)
lm_friendship_mod4   <- lmer(friendship_z~vincome+vedu+norelig*religion+vmigback+migration+polcenter+ideology_collapsed+selftrans+vgender+vage+vempstat +(religion|pid),data = df_vig)

screenreg(list(lm_friendship_mod1,lm_friendship_mod1.1,
               lm_friendship_mod2,lm_friendship_mod3,
               lm_friendship_mod4))


lm_friendship_mod5.1   <- lmer(friendship_z~vincome+vedu+norelig+religion+vmigback+migration+polcenter+ideology_collapsed+selftrans*self_transcendence+vgender+vage+vempstat +(selftrans|pid),data = df_vig)

lm_friendship_mod5.2   <- lmer(friendship_z~vincome+vedu+norelig+religion+vmigback+migration+polcenter+ideology_collapsed+selftrans*self_enhancement+vgender+vage+vempstat +(selftrans|pid),data = df_vig)

screenreg(list(lm_friendship_mod5.1,lm_friendship_mod5.2))

# Self-enhancement vs Self-transcendence
lm_friendship_mod5.2.1   <- lmer(friendship_z~vincome+vedu+norelig+religion+vmigback+migration+polcenter+ideology_collapsed+selftrans*self_transcendence+selftrans*self_enhancement+vgender+vage+vempstat +(selftrans|pid),data = df_vig)

lm_friendship_mod5.3   <- lmer(friendship_z~vincome+vedu+norelig+religion+vmigback+migration+polcenter+ideology_collapsed+selftrans*openness_change+vgender+vage+vempstat +(selftrans|pid),data = df_vig)
lm_friendship_mod5.4   <- lmer(friendship_z~vincome+vedu+norelig+religion+vmigback+migration+polcenter+ideology_collapsed+selftrans*conservation+vgender+vage+vempstat +(selftrans|pid),data = df_vig)

# Openess to change vs Conservation
lm_friendship_mod5.4.1   <- lmer(friendship_z~vincome+vedu+norelig+religion+vmigback+migration+polcenter+ideology_collapsed+selftrans+vgender+vage+vempstat+
                                 selftrans*openness_change+selftrans*conservation+(selftrans|pid),data = df_vig)

screenreg(list(lm_friendship_mod5.1,lm_friendship_mod5.2,lm_friendship_mod5.2.1,
               lm_friendship_mod5.3,lm_friendship_mod5.4,lm_friendship_mod5.4.1
               ))

screenreg(list(lm_friendship_mod5.2.1,
               lm_friendship_mod5.4.1
               ))
```
